---
output:
  html_document:
    mathjax: null
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    css: styles.css
params:
  dfResults: NA
  dfMetrics: NA
  dfGroups: NA
  lListings: NA
  nWindowDays: 90
---

```{r setup, include=FALSE}
library(dplyr)
library(gsm.kri)
library(plotly)
library(DT)
library(htmltools)
library(knitr)

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

dfResults <- params$dfResults
lListings <- params$lListings
nWindowDays <- params$nWindowDays

Mapped_Death <- lListings$Mapped_Death
Mapped_SUBJ <- lListings$Mapped_SUBJ

nEnrolled <- nrow(Mapped_SUBJ)
nPremature <- sum(!is.na(Mapped_Death$death_dy) & Mapped_Death$death_dy <= nWindowDays)
nPrematureRate <- ifelse(nEnrolled > 0, 100 * nPremature / nEnrolled, 0)
latest_snapshot <- max(dfResults$SnapshotDate)
has_premature <- nPremature > 0

# Consistency guard: the charts recompute premature status from Mapped_Death at
# nWindowDays; the patient listing trusts pat0015 Flag==2 rows (flagged at
# analysis-time meta.WindowDays). A divergence means nWindowDays != the window
# that produced dfResults -> charts and listing describe different windows.
nFlagged <- sum(
  dfResults$MetricID == "Analysis_pat0015" & dfResults$Flag == 2,
  na.rm = TRUE
)
if (nFlagged != nPremature) {
  pd_CheckWindowConsistency(nWindowDays, nPremature, nFlagged)
}
```

---
title: "Premature Deaths Overview"
subtitle: "Study: `r unique(Mapped_SUBJ$studyid)`"
date: "Snapshot Date: `r latest_snapshot`"
---

# Premature Deaths Overview

## Overview

::: flag-container
::: {.flag .flag-red}
<div> `r nPremature` Premature Death(s) </div>
:::

::: {.flag .flag-green}
<div> `r nEnrolled - nPremature` Alive at Window </div>
:::
:::

```{r overview, echo=FALSE, results='asis'}
cat(sprintf(
  "- **Configured window:** %d days\n
   - **Total enrolled:** %d\n
   - **Premature deaths (within window):** %d\n
   - **Premature death rate:** %.1f%%\n",
  nWindowDays, nEnrolled, nPremature, nPrematureRate
))
```

```{r empty-state, echo=FALSE, results='asis', eval=!has_premature}
cat("\n> **No premature deaths in window.** All charts and the patient listing are empty for this snapshot.\n")
```

## Study {.tabset .tabset-pills}

### Buckets
```{r study-buckets, echo=FALSE, eval=has_premature}
pd_BucketBar(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "studyid", strGroupLabel = "Study")
```

### Rand -> Death
```{r study-scatter, echo=FALSE, eval=has_premature}
pd_RandToDeathScatter(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "studyid", strGroupLabel = "Study", dSnapshotDate = latest_snapshot)
```

### Reasons
```{r study-reasons, echo=FALSE, eval=has_premature}
pd_ReasonDist(Mapped_Death, nWindowDays, nEnrolled = nEnrolled)
```

## Country {.tabset .tabset-pills}

### Buckets
```{r country-buckets, echo=FALSE, eval=has_premature}
pd_BucketBar(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "country", strGroupLabel = "Country")
```

### Rand -> Death
```{r country-scatter, echo=FALSE, eval=has_premature}
pd_RandToDeathScatter(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "country", strGroupLabel = "Country")
```

## Site {.tabset .tabset-pills}

### Buckets
```{r site-buckets, echo=FALSE, eval=has_premature}
pd_BucketBar(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "invid", strGroupLabel = "Site")
```

### Rand -> Death
```{r site-scatter, echo=FALSE, eval=has_premature}
pd_RandToDeathScatter(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "invid", strGroupLabel = "Site")
```

## Patient Listing
```{r patient-listing, echo=FALSE}
pd_PatientListing(dfResults, Mapped_Death)
```
