---
output:
  html_document:
    mathjax: null
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    css: styles.css
params:
  dfResults: NA
  lListings: NA
  strMetricID: "Analysis_kri0016"
  nMinAE: 20
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.retina = 2
)
library(dplyr)
library(ggplot2)
library(gt)
```

```{r compute}
dfDist <- AEGrading_SiteDistribution(
  params$lListings$Mapped_AE,
  params$lListings$Mapped_SUBJ,
  nMinAE = params$nMinAE
)

nSites <- dplyr::n_distinct(dfDist$GroupID)
nAE <- sum(dfDist$Count)
dfStudyGrade <- dfDist %>%
  dplyr::distinct(Grade, StudyProportion) %>%
  dplyr::arrange(Grade)
nStudyHigh <- sum(dfStudyGrade$StudyProportion[dfStudyGrade$Grade >= 3])

# Site-level results for the grading metric this report is reporting on.
dfMetricResults <- NULL
if (is.data.frame(params$dfResults) && nrow(params$dfResults) > 0) {
  dfMetricResults <- params$dfResults %>%
    dplyr::filter(
      .data$MetricID == params$strMetricID,
      .data$GroupLevel == "Site"
    )
}

strStudyLabel <- "Not specified"
dSnapshotLabel <- format(Sys.Date())
if (!is.null(dfMetricResults) && nrow(dfMetricResults) > 0) {
  if ("StudyID" %in% names(dfMetricResults)) {
    strStudyLabel <- unique(dfMetricResults$StudyID)[1]
  }
  if ("SnapshotDate" %in% names(dfMetricResults)) {
    dSnapshotLabel <- format(max(dfMetricResults$SnapshotDate))
  }
}
```

---
title: "AE Grading Overview"
subtitle: "Study: `r strStudyLabel`"
date: "Snapshot Date: `r dSnapshotLabel`"
---

```{=html}
<div style="border: 2px solid #c51f3f; border-left: 10px solid #c51f3f;
            background-color: #fdf0f2; color: #8a1129; border-radius: 4px;
            padding: 12px 16px; margin: 18px 0; font-size: 1.02em;">
  <strong style="color: #c51f3f; letter-spacing: 0.02em;">EXPERIMENTAL &mdash; FOR EXPLORATORY USE ONLY</strong><br />
  All findings should be independently confirmed.
</div>
```

# AE Grading Overview

This report examines how consistently investigator sites apply CTCAE severity
grading to adverse events. It is a companion to the site-level grading KRIs
`kri0016` (High-Grade AE Proportion) and `kri0017` (Low-Grade AE Proportion),
and asks a single question: does a site's distribution of Grade 1–5 events look
like the rest of the study? Sites that grade nearly everything as Grade 1, or
nearly everything as Grade 3/4, stand out against their peers.

`r nAE` graded adverse events across `r nSites` sites met the minimum volume
threshold of `r params$nMinAE` graded AEs per site. Study-wide,
**`r sprintf("%.1f%%", nStudyHigh * 100)`** of adverse events are Grade 3 or higher.

## Study-wide grade distribution

```{r study-dist}
dfStudyGrade %>%
  dplyr::mutate(
    Grade = paste("Grade", Grade),
    Events = round(StudyProportion * nAE),
    StudyProportion = scales::percent(StudyProportion, accuracy = 0.1)
  ) %>%
  dplyr::select(Grade, Events, `% of all AEs` = StudyProportion) %>%
  gt::gt() %>%
  gt::tab_options(table.width = gt::pct(60))
```

# Grade distribution by site

Each bar is one site's severity mix, sorted by the proportion of Grade 3+ events.
Sites at the top report the highest share of severe events; sites at the bottom
report the lowest. The dashed line marks the study-wide Grade 3+ proportion —
bars that break well away from it in either direction are the sites whose grading
behaviour differs from their peers.

```{r grade-by-site, fig.width = 10, fig.height = 12}
Visualize_GradeBySite(dfDist, dfFlagged = dfMetricResults)
```

## Flagged sites

```{r flagged-sites}
if (is.null(dfMetricResults) || nrow(dfMetricResults) == 0) {
  cat("No metric results were supplied, so no sites are flagged.")
} else {
  dfF <- dfMetricResults %>%
    dplyr::filter(!is.na(Flag), Flag != 0) %>%
    dplyr::arrange(desc(abs(Score)))

  if (nrow(dfF) == 0) {
    cat("No sites were flagged by the grading metric.")
  } else {
    nStudyMetric <- sum(dfMetricResults$Numerator, na.rm = TRUE) /
      sum(dfMetricResults$Denominator, na.rm = TRUE)

    dfF %>%
      dplyr::transmute(
        Site = GroupID,
        Numerator = Numerator,
        `Total AEs` = Denominator,
        `Site %` = scales::percent(Metric, accuracy = 0.1),
        `Study %` = scales::percent(nStudyMetric, accuracy = 0.1),
        `Z-score` = round(Score, 2),
        Direction = ifelse(Flag > 0, "Over-grading", "Under-grading")
      ) %>%
      gt::gt() %>%
      gt::tab_options(table.width = gt::pct(100)) %>%
      gt::tab_source_note(
        "Sites flagged by the grading metric on a two-sided adjusted z-score. Over-grading means the site reports a higher proportion of the graded events of interest than the study; under-grading, a lower proportion."
      )
  }
}
```

# Method notes and limitations

- **Grades are treated as reported.** No re-derivation from lab values or
  outcome data is attempted; the report measures internal consistency across
  sites, not clinical correctness.
- **The study is its own comparator.** If grading drifts study-wide, this report
  will not detect it — every site is compared to the study average.
- **The overall severity mix is a blunt instrument.** A site can report a
  perfectly average proportion of severe events while still grading individual
  event types inconsistently. Detecting that requires comparing sites against
  the study term by term, which is not part of this report.
- **Small sites are excluded.** Sites below `r params$nMinAE` graded AEs are
  dropped from the chart, so a small site with a genuine grading problem may not
  appear at all.
