---
output:
  html_document:
    mathjax: null
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    css: styles.css
params:
  dfResults: NA
  dfMetrics: NA
  dfGroups: NA
  lListings: NA
  nWindowDays: 90
---

```{r setup, include=FALSE}
library(dplyr)
library(gsm.kri)
library(plotly)
library(DT)
library(htmltools)
library(knitr)
library(jsonlite)

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

dfResults <- params$dfResults
lListings <- params$lListings
nWindowDays <- params$nWindowDays

Mapped_Death <- lListings$Mapped_Death
Mapped_SUBJ <- lListings$Mapped_SUBJ

# Country → site lookup for JS filtering (all enrolled sites in the country)
country_site_map <- Mapped_SUBJ %>%
  dplyr::distinct(country, invid) %>%
  dplyr::group_by(country) %>%
  dplyr::summarise(sites = list(invid), .groups = "drop") %>%
  tibble::deframe() %>%
  jsonlite::toJSON(auto_unbox = FALSE)

# Premature-death cohort (deaths within nWindowDays, joined to subject country/
# site), computed once and reused for the count and the per-country banner.
dfPrematureCohort <- pd_PrematureCohort(Mapped_Death, Mapped_SUBJ, nWindowDays)

# Per-country count of enrolled sites with >=1 premature death, for the filter
# banner's "N/M sites with at least 1 premature death" headline. Only the count
# is consumed (as the numerator over the country's enrolled-site total), so we
# don't carry the site-id arrays.
country_premature_count <- dfPrematureCohort %>%
  dplyr::distinct(.data$country, .data$invid) %>%
  dplyr::count(.data$country) %>%
  tibble::deframe() %>%
  jsonlite::toJSON(auto_unbox = TRUE)

nEnrolled <- nrow(Mapped_SUBJ)
nPremature <- nrow(dfPrematureCohort)
nPrematureRate <- ifelse(nEnrolled > 0, 100 * nPremature / nEnrolled, 0)
latest_snapshot <- max(dfResults$SnapshotDate)
has_premature <- nPremature > 0

# Consistency guard: the charts recompute premature status from Mapped_Death at
# nWindowDays; the patient listing trusts pat0015 Flag==2 rows (flagged at
# analysis-time meta.WindowDays). A divergence means nWindowDays != the window
# that produced dfResults -> charts and listing describe different windows.
nFlagged <- sum(
  dfResults$MetricID == "Analysis_pat0015" & dfResults$Flag == 2,
  na.rm = TRUE
)
if (nFlagged != nPremature) {
  pd_CheckWindowConsistency(nWindowDays, nPremature, nFlagged)
}
```

---
title: "Premature Deaths Overview"
subtitle: "Study: `r unique(Mapped_SUBJ$studyid)`"
date: "Snapshot Date: `r latest_snapshot`"
---

# Premature Deaths Overview

## Overview

::: flag-container
::: {.flag .flag-red}
<div> `r nPremature` Premature Death(s) </div>
:::

::: {.flag .flag-green}
<div> `r nEnrolled - nPremature` Alive at Window </div>
:::
:::

```{r overview, echo=FALSE, results='asis'}
cat(sprintf(
  "- **Configured window:** %d days\n
   - **Total enrolled:** %d\n
   - **Premature deaths (within window):** %d\n
   - **Premature death rate:** %.1f%%\n",
  nWindowDays, nEnrolled, nPremature, nPrematureRate
))
```

```{r empty-state, echo=FALSE, results='asis', eval=!has_premature}
cat("\n> **No premature deaths in window.** All charts and the patient listing are empty for this snapshot.\n")
```

```{r mode-toggle, echo=FALSE, results='asis', eval=has_premature}
cat('
<div id="pd-mode-toggle" style="margin:12px 0;">
  <span style="font-size:13px; color:#555; margin-right:8px;">Bucket bars:</span>
  <button id="pd-mode-count" onclick="pdSetMode(\'count\')" style="background:#1a73e8; color:white; border:none; border-radius:4px; padding:4px 14px; cursor:pointer; font-size:12px;">Count</button>
  <button id="pd-mode-pct" onclick="pdSetMode(\'pct\')" style="background:#cfd8dc; color:#37474f; border:none; border-radius:4px; padding:4px 14px; cursor:pointer; font-size:12px;">%</button>
</div>
')
```

```{r rangeslider-css, echo=FALSE, results='asis', eval=has_premature}
# Hide each bucket bar's range-slider mini-preview, leaving a scroll-only track.
# Scoped to the three bucket-bar container ids so it never reaches another
# gsm.kri report sharing styles.css. A stylesheet rule (not inline JS) is used
# so it re-matches the slider DOM that Plotly.react rebuilds on every filter.
cat('
<style>
#pd-study-buckets .rangeslider-rangeplot,
#pd-country-buckets .rangeslider-rangeplot,
#pd-site-buckets .rangeslider-rangeplot { display: none !important; }
</style>
')
```

## Study {.tabset .tabset-pills}

### Buckets
```{r study-buckets, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-study-buckets",
  pd_BucketBar(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "studyid", strGroupLabel = "Study", bRangeSlider = TRUE)
)
```

### Rand -> Death
```{r study-scatter, echo=FALSE, eval=has_premature}
pd_RandToDeathScatter(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "studyid", strGroupLabel = "Study", dSnapshotDate = latest_snapshot)
```

### Reasons
```{r study-reasons, echo=FALSE, eval=has_premature}
pd_ReasonDist(Mapped_Death, nWindowDays, nEnrolled = nEnrolled)
```

## Country {.tabset .tabset-pills}

### Buckets
```{r country-buckets, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-country-buckets",
  pd_BucketBar(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "country", strGroupLabel = "Country", strOuterCol = "studyid", bRangeSlider = TRUE)
)
```

### Rand -> Death
```{r country-scatter, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-country-scatter",
  pd_RandToDeathScatter(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "country", strGroupLabel = "Country", strOuterCol = "studyid")
)
```

## Site {.tabset .tabset-pills}

<div id="pd-filter-banner" style="display:none; background:#e3f2fd; border:1px solid #90caf9; border-radius:6px; padding:10px 16px; margin:16px 0; flex-direction:column; gap:8px;">
<div id="pd-filter-country-row" style="display:none; align-items:center; justify-content:space-between;">
<span id="pd-filter-text" style="font-size:13px; color:#1565c0;"></span>
<button id="pd-filter-reset" onclick="pdResetFilter()" style="background:#1a73e8; color:white; border:none; border-radius:4px; padding:4px 12px; cursor:pointer; font-size:12px;">✕ Show All Sites</button>
</div>
<div id="pd-filter-site-row" style="display:none; align-items:center; justify-content:space-between;">
<span id="pd-site-filter-text" style="font-size:13px; color:#1565c0;"></span>
<button id="pd-site-filter-reset" onclick="pdResetSiteFilter()" style="background:#1a73e8; color:white; border:none; border-radius:4px; padding:4px 12px; cursor:pointer; font-size:12px;">✕ Clear Site</button>
</div>
</div>

### Buckets
```{r site-buckets, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-site-buckets",
  pd_BucketBar(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "invid", strGroupLabel = "Site", strOuterCol = "country", strOuterLabel = "Country", bRangeSlider = TRUE)
)
```

### Rand -> Death
```{r site-scatter, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-site-scatter",
  pd_RandToDeathScatter(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "invid", strGroupLabel = "Site", strOuterCol = "country")
)
```

## Patient Listing
```{r patient-listing, echo=FALSE}
pd_PatientListing(dfResults, Mapped_Death, Mapped_SUBJ)
```

```{r filter-js, echo=FALSE, results='asis', eval=has_premature}
cat(paste0('
<script>
(function() {
  var countrySiteMap = ', country_site_map, ';
  var countryPrematureCount = ', country_premature_count, ';
  var activeCountry = null;
  var activeSite = null;

  // Find the plotly div inside a container (returns null until Plotly has
  // initialized the widget and attached its event system).
  function getPlotlyDiv(containerId) {
    var container = document.getElementById(containerId);
    if (!container) return null;
    var el = container.querySelector(".plotly");
    if (!el || !el.on) return null;
    return el;
  }

  // The interactive charts carry their category dimension as a 2-D
  // multicategory axis [[outer],[inner]] -- bars on x, scatters on y. This
  // returns the inner tier (the site / country labels) regardless of which axis
  // holds it, so the helpers below never branch on chart shape.
  function catLabels(tr) {
    if (Array.isArray(tr.x) && Array.isArray(tr.x[0])) return tr.x[1];
    if (Array.isArray(tr.y) && Array.isArray(tr.y[0])) return tr.y[1];
    return tr.x; // flat fallback (defensive; interactive charts are 2-D)
  }

  // Restore every bar in a chart to full opacity (one batched restyle).
  function undimBars(containerId) {
    var el = getPlotlyDiv(containerId);
    if (!el) return;
    var opacities = el.data.map(function(tr) {
      return catLabels(tr).map(function() { return 1.0; });
    });
    Plotly.restyle(el, {"marker.opacity": opacities}, el.data.map(function(_, i) { return i; }));
  }

  // Dim every bar except those whose category equals `value` (one batched
  // restyle across all traces).
  function dimBarsExcept(el, value) {
    var opacities = el.data.map(function(tr) {
      return catLabels(tr).map(function(v) { return v === value ? 1.0 : 0.3; });
    });
    Plotly.restyle(el, {"marker.opacity": opacities}, el.data.map(function(_, i) { return i; }));
  }

  // Attach click handler to country buckets chart (retry until Plotly ready, max 20)
  var attachRetries = 0;
  function attachCountryClick() {
    var el = getPlotlyDiv("pd-country-buckets");
    if (!el) {
      if (++attachRetries < 20) setTimeout(attachCountryClick, 500);
      return;
    }
    el.on("plotly_click", function(data) {
      var country = data.points[0].x[1]; // multicategory click -> [study, country]
      if (country === activeCountry) {
        pdResetFilter();
      } else {
        applyFilter(country);
      }
    });
  }

  function applyFilter(country) {
    activeCountry = country;
    var sites = countrySiteMap[country] || [];
    var prematureCount = countryPrematureCount[country] || 0;

    // Show the country banner row. The headline reports how many of the country\'s
    // enrolled sites had at least one premature death (premature-site count over
    // the enrolled-site total).
    document.getElementById("pd-filter-country-row").style.display = "flex";
    document.getElementById("pd-filter-text").innerHTML =
      "\\ud83d\\udd0d <strong>Showing " + country + "</strong> \\u2014 " +
      prematureCount + "/" + sites.length +
      " sites with at least 1 premature death";
    updateBannerVisibility();

    // Highlight country bar: dim non-selected
    highlightCountryBar(country);

    // Filter country scatter to selected country only
    filterPlotlyChart("pd-country-scatter", [country]);

    // Filter site buckets + scatter to this country\'s sites
    filterPlotlyChart("pd-site-buckets", sites);
    filterPlotlyChart("pd-site-scatter", sites);

    // The site-buckets re-render above wiped any site-bar opacity highlight;
    // re-apply it so an active, independent site selection stays visible.
    if (activeSite) highlightSiteBar(activeSite);

    // Re-derive the listing from all active filters (site > country precedence).
    applyListingFilter();
  }

  function highlightCountryBar(country) {
    var el = getPlotlyDiv("pd-country-buckets");
    if (!el) return;
    dimBarsExcept(el, country);
  }

  // Show/hide the banner container based on whether either row is active.
  function updateBannerVisibility() {
    var banner = document.getElementById("pd-filter-banner");
    banner.style.display = (activeCountry || activeSite) ? "flex" : "none";
  }

  // Single owner of the patient-listing column search. Only one search can be
  // held on the invid column, so both filters route through here. Precedence:
  // an active site wins over an active country (site is more specific).
  function applyListingFilter() {
    var tables = document.querySelectorAll(".dataTable");
    if (tables.length === 0) return;
    var dtApi = $(tables[tables.length - 1]).DataTable();
    var sites = null;
    if (activeSite) {
      sites = [activeSite];
    } else if (activeCountry) {
      sites = countrySiteMap[activeCountry] || [];
    }
    if (sites) {
      var regex = "^(" + sites.join("|") + ")$";
      dtApi.column("invid:name").search(regex, true, false).draw();
    } else {
      dtApi.column("invid:name").search("").draw();
    }
  }

  // Attach click handler to site buckets chart (retry until Plotly ready, max 20)
  var siteAttachRetries = 0;
  function attachSiteClick() {
    var el = getPlotlyDiv("pd-site-buckets");
    if (!el) {
      if (++siteAttachRetries < 20) setTimeout(attachSiteClick, 500);
      return;
    }
    el.on("plotly_click", function(data) {
      var invid = data.points[0].x[1]; // multicategory click -> [country, site]
      if (invid === activeSite) {
        pdResetSiteFilter();
      } else {
        applySiteFilter(invid);
      }
    });
  }

  function applySiteFilter(invid) {
    activeSite = invid;
    document.getElementById("pd-filter-site-row").style.display = "flex";
    document.getElementById("pd-site-filter-text").innerHTML =
      "\\ud83d\\udd0d <strong>Showing site " + invid + "</strong> \\u2014 patient listing filtered";
    updateBannerVisibility();
    highlightSiteBar(invid);
    applyListingFilter();
  }

  function highlightSiteBar(invid) {
    var el = getPlotlyDiv("pd-site-buckets");
    if (!el) return;
    // Seed the filter cache with CLEAN (un-dimmed) data BEFORE dimming below.
    // pd-site-buckets is the one chart that is both a highlight target and a
    // filter target: if a site is clicked before any country filter,
    // filterPlotlyChart would otherwise lazily cache this dimmed chart as the
    // "original", and a later country reset would restore a permanently-dimmed
    // chart. cacheOriginal is idempotent, so a clean cache (seeded here on a
    // site-first click, or by filterPlotlyChart on a country-first click) is
    // never overwritten.
    cacheOriginal(el, "pd-site-buckets");
    // If the selected site isn\'t currently rendered (e.g. a country filter is
    // showing a different country\'s sites), leave opacities untouched rather
    // than dimming every bar to 0.3.
    var present = el.data.some(function(tr) { return catLabels(tr).indexOf(invid) >= 0; });
    if (!present) return;
    dimBarsExcept(el, invid);
  }

  // Global reset for the site filter (called by the site row\'s button onclick)
  window.pdResetSiteFilter = function() {
    activeSite = null;
    document.getElementById("pd-filter-site-row").style.display = "none";
    updateBannerVisibility();

    // Un-dim site bars
    undimBars("pd-site-buckets");

    // Re-derive the listing from any remaining active filter (e.g. country).
    applyListingFilter();
  };

  // Store original trace data + layout for each chart on first filter
  var originalData = {};
  var originalLayout = {};

  // Cache a chart\'s clean trace data + layout the first time we touch it, so a
  // later reset can restore the un-filtered, un-dimmed version. Idempotent: a
  // second call never overwrites an existing (clean) cache.
  function cacheOriginal(el, containerId) {
    if (!originalData[containerId]) {
      originalData[containerId] = JSON.parse(JSON.stringify(el.data));
    }
    if (!originalLayout[containerId]) {
      originalLayout[containerId] = JSON.parse(JSON.stringify(el.layout));
    }
  }

  function filterPlotlyChart(containerId, allowedValues) {
    var el = getPlotlyDiv(containerId);
    if (!el) return;
    cacheOriginal(el, containerId);
    var orig = originalData[containerId];
    var filtered = orig.map(function(trace) {
      // The multicategory axis is the one whose first entry is itself an array
      // ([[outer],[inner]]); its inner tier holds the labels we filter on. Bars
      // carry it on x, scatters on y.
      var axis = (Array.isArray(trace.x) && Array.isArray(trace.x[0])) ? "x"
               : (Array.isArray(trace.y) && Array.isArray(trace.y[0])) ? "y"
               : null;
      if (!axis) return trace;
      var inner = trace[axis][1];
      var indices = [];
      inner.forEach(function(val, idx) {
        if (allowedValues.indexOf(val) >= 0) indices.push(idx);
      });
      var valueAxis = axis === "x" ? "y" : "x";
      var newTrace = Object.assign({}, trace);
      // One `indices` list reindexes every per-point array in lockstep: both
      // tiers of the category axis, the numeric value axis, and customdata --
      // index i addresses the same data point in all of them.
      newTrace[axis] = [
        indices.map(function(i) { return trace[axis][0][i]; }),
        indices.map(function(i) { return trace[axis][1][i]; })
      ];
      if (trace[valueAxis]) {
        newTrace[valueAxis] = indices.map(function(i) { return trace[valueAxis][i]; });
      }
      if (trace.text) newTrace.text = indices.map(function(i) { return trace.text[i]; });
      if (trace.customdata) newTrace.customdata = indices.map(function(i) { return trace.customdata[i]; });
      return newTrace;
    });
    // A reindexed multicategory axis re-derives its own ticks from the data, so
    // the empty-slot workaround the flat axis needed is gone. Clone the cached
    // layout so Plotly.react cannot mutate the stored original.
    Plotly.react(el, filtered, JSON.parse(JSON.stringify(originalLayout[containerId])));
    // Only the bucket bars carry [count, pct]; scatters pack a hover string in
    // customdata, so applyMode() must never run on them (it would garble y / the
    // axis). PD_BUCKET_CHARTS already lists exactly the three bucket containers.
    // Unconditional (not just % mode): restyle mutates el.data in place, so a
    // cache seeded while % mode was active holds % y values; re-deriving y from
    // customdata on every react makes that polluted cache harmless in both modes.
    if (PD_BUCKET_CHARTS.indexOf(containerId) >= 0) applyMode(el);
  }

  // Global reset for the country filter (called by the country row\'s button onclick)
  window.pdResetFilter = function() {
    activeCountry = null;

    // Hide the country banner row (the site row stays as-is)
    document.getElementById("pd-filter-country-row").style.display = "none";
    updateBannerVisibility();

    // Reset country bar opacity
    undimBars("pd-country-buckets");

    // Reset charts the country filter owns
    resetPlotlyChart("pd-country-scatter");
    resetPlotlyChart("pd-site-buckets");
    resetPlotlyChart("pd-site-scatter");

    // The site-buckets reset above wiped any site-bar highlight; re-apply it
    // if a site filter is still active.
    if (activeSite) highlightSiteBar(activeSite);

    // Re-derive the listing from any remaining active filter (keeps a site).
    applyListingFilter();
  };

  function resetPlotlyChart(containerId) {
    var el = getPlotlyDiv(containerId);
    if (!el || !originalData[containerId]) return;
    // Restore the original layout so the full categorical axis returns
    Plotly.react(el, originalData[containerId], originalLayout[containerId] || el.layout);
    // Bucket charts only -- see the filterPlotlyChart note: scatters are filter
    // targets too, and applyMode() would corrupt their string customdata / y-axis.
    // Unconditional for the same reason as filterPlotlyChart: the cached
    // "original" may carry %-mode y values; applyMode re-derives the right y
    // for the CURRENT mode from customdata either way.
    if (PD_BUCKET_CHARTS.indexOf(containerId) >= 0) applyMode(el);
  }

  // ---- Count <-> % toggle for the three bucket bars -----------------------
  // pd_BucketBar packs [count, pct] per point into customdata; y is always
  // re-derived from it, so the mode is stateless and survives the Plotly.react
  // the filters trigger (re-applied at the tail of every react below).
  var pdMode = "count";
  var PD_BUCKET_CHARTS = ["pd-study-buckets", "pd-country-buckets", "pd-site-buckets"];

  function applyMode(el) {
    if (!el || !el.data) return;
    var slot = pdMode === "pct" ? 1 : 0;
    var traceIndices = el.data.map(function(_, idx) { return idx; });
    var ys = el.data.map(function(tr) {
      return (tr.customdata || []).map(function(cd) { return cd[slot]; });
    });
    // One atomic data+layout update (single redraw) instead of restyle+relayout:
    // avoids the bars-resized-but-axis-stale flicker frame, which the filter hooks
    // would otherwise paint on every react in % mode. range:null clears the fixed
    // [0,100] so autorange unambiguously recomputes the Subjects scale on the way back.
    var layoutUpdate = pdMode === "pct"
      ? {"yaxis.title.text": "% of group", "yaxis.ticksuffix": "%", "yaxis.range": [0, 100]}
      : {"yaxis.title.text": "Subjects", "yaxis.ticksuffix": "", "yaxis.autorange": true, "yaxis.range": null};
    Plotly.update(el, {y: ys}, layoutUpdate, traceIndices);
  }

  window.pdSetMode = function(mode) {
    pdMode = mode;
    // Flip text color WITH background: white text on the inactive light-grey
    // (#cfd8dc) would be illegible, so the inactive side gets dark text.
    var btnCount = document.getElementById("pd-mode-count");
    var btnPct = document.getElementById("pd-mode-pct");
    btnCount.style.background = mode === "count" ? "#1a73e8" : "#cfd8dc";
    btnCount.style.color = mode === "count" ? "white" : "#37474f";
    btnPct.style.background = mode === "pct" ? "#1a73e8" : "#cfd8dc";
    btnPct.style.color = mode === "pct" ? "white" : "#37474f";
    PD_BUCKET_CHARTS.forEach(function(id) { applyMode(getPlotlyDiv(id)); });
  };

  // Initialize when DOM is ready
  function attachClickHandlers() {
    attachCountryClick();
    attachSiteClick();
  }
  if (document.readyState === "complete") {
    attachClickHandlers();
  } else {
    window.addEventListener("load", attachClickHandlers);
  }
})();
</script>
'))
```
