---
# pagetitle sets only the HTML <head><title> (browser tab); it does NOT render a
# visible heading, so it neither duplicates the body H1 nor affects the
# knit_child pkgdown embed (which ignores this front matter). The visible title +
# dynamic subtitle are emitted in the body.
pagetitle: "Premature Deaths Overview"
output:
  html_document:
    mathjax: null
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    css: styles.css
params:
  dfResults: NA
  dfMetrics: NA
  dfGroups: NA
  lListings: NA
  nWindowDays: 90
---

```{r setup, include=FALSE}
library(dplyr)
library(gsm.kri)
library(plotly)
library(DT)
library(htmltools)
library(knitr)
library(jsonlite)

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

dfResults <- params$dfResults
lListings <- params$lListings
nWindowDays <- params$nWindowDays

Mapped_Death <- lListings$Mapped_Death
Mapped_SUBJ <- lListings$Mapped_SUBJ
Mapped_STUDCOMP <- lListings$Mapped_STUDCOMP
Mapped_EXCLUSION <- lListings$Mapped_EXCLUSION
Mapped_AE <- lListings$Mapped_AE
Mapped_Randomization <- lListings$Mapped_Randomization

# In production Mapped_SUBJ has no randomization date; source it from
# Mapped_Randomization (passed in lListings). Then drop subjects with no
# randomization date -- they have no position on the randomization-anchored
# timeline, so they must not be counted in the bars yet dropped from the scatter.
if (!"rgmn_dt" %in% names(Mapped_SUBJ) && !is.null(Mapped_Randomization)) {
  Mapped_SUBJ <- dplyr::left_join(
    Mapped_SUBJ,
    dplyr::distinct(dplyr::select(Mapped_Randomization, "subjid", "rgmn_dt")),
    by = "subjid"
  )
}
if ("rgmn_dt" %in% names(Mapped_SUBJ)) {
  Mapped_SUBJ <- dplyr::filter(Mapped_SUBJ, !is.na(.data$rgmn_dt))
}

# Reporting snapshot drives follow-up (the two "alive" categories), so it is
# defined here, ahead of the single classification of every enrolled subject.
latest_snapshot <- max(dfResults$SnapshotDate)

# Single classification of every enrolled subject (the SOT for all charts).
dfClassified <- pd_Classify(
  dfSubjects = Mapped_SUBJ,
  dfDeath = Mapped_Death,
  dfStudComp = Mapped_STUDCOMP,
  nWindowDays = nWindowDays,
  dSnapshotDate = latest_snapshot
)

# Build the scatter's per-point hover + customdata once; the study/country/site
# views reuse it (pd_ScatterData is idempotent, so each scatter call skips the rebuild).
dfScatter <- gsm.kri:::pd_ScatterData(dfClassified)

# Study-wide fixed scatter range, shared by the study/country/site views (AXIS-1).
# Derived from the data (not hardcoded); a 5% pad keeps boundary points off the edge.
x_max <- max(c(dfClassified$x_anchor, nWindowDays), na.rm = TRUE)
y_max <- max(c(dfClassified$follow_up, nWindowDays), na.rm = TRUE)
vXRange <- c(0, x_max * 1.05)
vYRange <- c(0, y_max * 1.05)

# Country → site lookup for JS filtering (all enrolled sites in the country).
# Built from dfClassified -- the same cohort the bucket bars use -- so its keys
# are exactly the bars' country labels (incl. "Unknown"); clicking any bar always
# resolves to that country's sites instead of an empty filter.
country_site_map <- dfClassified %>%
  dplyr::distinct(country, invid) %>%
  dplyr::group_by(country) %>%
  dplyr::summarise(sites = list(invid), .groups = "drop") %>%
  tibble::deframe() %>%
  jsonlite::toJSON(auto_unbox = FALSE)

has_eligibility <- !is.null(Mapped_EXCLUSION) && "Source" %in% names(Mapped_EXCLUSION)

# Overview summary numbers, computed once from the classified cohort (the single
# source of truth). Driving nEnrolled / nPremature from here -- not a separate
# pd_PrematureCohort count -- means the Overview table, the empty-state, every
# chart's eval=has_premature gate, and the window-consistency guard below all
# describe the one cohort the bucket bars and scatter render, so they can never
# drift apart (a duplicate death row or a death for an unmapped subject no longer
# makes the guard and the table disagree).
stats <- pd_OverviewStats(dfClassified, Mapped_EXCLUSION, nWindowDays)
nEnrolled <- stats$nEnrolled
nPremature <- stats$nPremature
nPrematureRate <- stats$nPrematureRate
has_premature <- nPremature > 0

# Per-country enrolled counts off the classified cohort (same basis as nEnrolled).
# dfClassified$country is already "Unknown"-labelled (pd_Classify), so these keys
# match pd_ReasonByCountry's split and the country->site map by construction.
enrolled_by_country <- dfClassified %>%
  dplyr::count(country, name = "n") %>%
  tibble::deframe()

# Reason aggregate computed ONCE: per-country slices + "__ALL__", each with prebuilt
# hover (incl. % of enrolled). The country-reasons widget receives these rows as
# its reactive map and swaps slices client-side on a country click.
reason_data <- pd_ReasonByCountry(Mapped_Death, Mapped_SUBJ, nWindowDays,
                                  nEnrolledByCountry = enrolled_by_country,
                                  nEnrolled = nEnrolled)

# Study-discontinuation caveat, shared verbatim by the Study Buckets and the
# Study Rand -> Death tabs (single source of truth so the embedded nWindowDays
# can't drift between the two placements).
study_discont_note <- paste0(
  "\n> **Study discontinuation** is taken from study-completion records (`studcomp`): a subject is counted here when their record indicates discontinuation within ",
  nWindowDays,
  " days of randomization for a reason other than death. Deaths within ",
  nWindowDays,
  " days appear under *Death within ",
  nWindowDays,
  " days*; subjects still on study appear under the *Alive* categories. Discontinuation timing is approximated from the study-completion record date.\n"
)

# Consistency guard: the charts recompute premature status from Mapped_Death at
# nWindowDays; the patient listing trusts pat0015 Flag==2 rows (flagged at
# analysis-time meta.WindowDays). A divergence means nWindowDays != the window
# that produced dfResults -> charts and listing describe different windows.
nFlagged <- sum(
  dfResults$MetricID == "Analysis_pat0015" & dfResults$Flag == 2,
  na.rm = TRUE
)
# Warns only on a mismatch; the comparison lives inside the helper now.
pd_CheckWindowConsistency(nWindowDays, nPremature, nFlagged)
```

# Premature Deaths Overview

```{r overview-subtitle, echo=FALSE, results='asis'}
# Dynamic subtitle emitted as real markdown. A second "--- title/subtitle/date ---"
# block here is NOT front matter -- pandoc only honours the top header, so it would
# render as a literal "title:" line + rule. The H1 above is the title; this chunk
# renders in both the standalone report and the knit_child pkgdown embed.
cat(sprintf(
  "**Study:** %s  \n*Snapshot Date: %s*\n\n",
  paste(unique(Mapped_SUBJ$studyid), collapse = ", "),
  latest_snapshot
))
```

```{r filter-strip-css, echo=FALSE, results='asis'}
# The chip strip's styling ships as an inline <style> block HERE, not via
# styles.css, so it survives every host context. The standalone report links
# styles.css, but the pkgdown example embeds this report through knit_child and
# does NOT load styles.css -- there the chips would render unstyled and
# non-sticky. Literal hex (no var(--...) tokens) for the same reason: the :root
# tokens defined in styles.css aren't present in the embedded context.
cat('
<style>
.pd-filter-strip { position: sticky; top: 48px; z-index: 1029; display: none; align-items: center; flex-wrap: wrap; gap: 10px; background-color: #f1f7fe; border-bottom: 1px solid #cfe3fb; padding: 8px 14px; margin: 0 0 16px; }
.pd-filter-eyebrow { font-size: 11px; font-weight: 600; letter-spacing: 0.08em; text-transform: uppercase; color: #5b7193; }
.pd-filter-chip { display: inline-flex; align-items: center; gap: 6px; background-color: #ffffff; border: 1px solid #3C587F; border-radius: 16px; padding: 3px 6px 3px 12px; font-size: 13px; color: #3C587F; }
.pd-chip-value { font-weight: 600; }
.pd-filter-chip button { display: inline-flex; align-items: center; justify-content: center; width: 18px; height: 18px; padding: 0; border: none; border-radius: 50%; background-color: transparent; color: #3C587F; font-size: 13px; line-height: 1; cursor: pointer; }
.pd-filter-chip button:hover { background-color: #3C587F; color: #ffffff; }
.pd-filter-chip button:focus-visible { outline: 2px solid #3C587F; outline-offset: 2px; }
</style>
')
```

```{r filter-strip, echo=FALSE}
# Sticky cross-filter strip: one chip per active country/site filter, shown by
# the filter-js chunk as selections change. Built with htmltools (not raw HTML)
# so pandoc doesn't wrap the inline chips in a <p>, which would break the flex
# row and add stray paragraph margins. Hidden (CSS display:none) until a filter
# is active.
htmltools::tags$div(
  id = "pd-filter-banner", class = "pd-filter-strip",
  htmltools::tags$span(class = "pd-filter-eyebrow", "Filtering"),
  htmltools::tags$span(
    id = "pd-filter-country-chip", class = "pd-filter-chip", style = "display:none;",
    htmltools::tags$span(
      class = "pd-chip-label", "Country: ",
      htmltools::tags$span(id = "pd-filter-country-value", class = "pd-chip-value")
    ),
    htmltools::tags$button(
      id = "pd-filter-reset", onclick = "pdResetFilter()",
      `aria-label` = "Clear country filter", htmltools::HTML("&times;")
    )
  ),
  htmltools::tags$span(
    id = "pd-filter-site-chip", class = "pd-filter-chip", style = "display:none;",
    htmltools::tags$span(
      class = "pd-chip-label", "Site: ",
      htmltools::tags$span(id = "pd-filter-site-value", class = "pd-chip-value")
    ),
    htmltools::tags$button(
      id = "pd-site-filter-reset", onclick = "pdResetSiteFilter()",
      `aria-label` = "Clear site filter", htmltools::HTML("&times;")
    )
  )
)
```

## Overview

Premature death analysis supports early identification of deaths occurring within ≤`r nWindowDays` days of randomization, enabling timely detection of potential eligibility concerns and emerging safety risks.

```{r overview-table, echo=FALSE}
# Ineligible needs eligibility data (Mapped_EXCLUSION); when it is absent we show
# a dash rather than 0, which would falsely assert zero ineligible deaths.
ineligible_cell <- if (stats$has_eligibility) {
  sprintf("%d (%.1f%%)", stats$nIneligible, stats$nIneligibleRate)
} else {
  "—"
}
# Headline total over a severity-keyed ledger: the two windows stack as child
# rows under the total, each led by its bucket colour (death30 =
# colorScheme("red","dark") #FF5859, death3190 = colorScheme("amber","dark")
# #FEAA02 -- the exact hues the bucket bars and scatter use), so the cell doubles
# as their legend. The table's full-grid borders fence the cell and right-
# aligned counts make 22 + 24 = 46 read as additive. Literal ≤/– glyphs (not
# &le;/&ndash;) because pandoc's html4 output preserves entities verbatim;
# swatches are styled <div>s, so no entities and no unimported font weights are
# relied on. Counts come from the one classified cohort, so the split cannot
# drift from the total.
premature_cell <- sprintf(
  paste0(
    "<div style='font-size:1.1em'>%d <span style='color:#666;font-size:smaller'>(%.1f%%)</span></div>",
    "<div style='display:inline-block;text-align:left;margin-top:3px;font-size:smaller'>",
    "<div><span style='display:inline-block;width:9px;height:9px;background:#FF5859;margin-right:6px'></span>",
    "<b style='display:inline-block;min-width:1.4em;text-align:right'>%d</b> ≤30 days</div>",
    "<div><span style='display:inline-block;width:9px;height:9px;background:#FEAA02;margin-right:6px'></span>",
    "<b style='display:inline-block;min-width:1.4em;text-align:right'>%d</b> 31–90 days</div>",
    "</div>"
  ),
  stats$nPremature, stats$nPrematureRate, stats$nDeath30, stats$nDeath3190
)
knitr::kable(
  data.frame(
    "Total enrolled" = stats$nEnrolled,
    "Total sites with enrolled participants" = stats$nSites,
    "Premature Death(s)" = premature_cell,
    "Participants Ineligible + Premature Death" = ineligible_cell,
    check.names = FALSE
  ),
  format = "html",
  escape = FALSE,
  align = "r",
  table.attr = "class=\"table table-bordered\""
)
```

```{r empty-state, echo=FALSE, results='asis', eval=!has_premature}
cat("\n> **No premature deaths in window.** All charts and the patient listing are empty for this snapshot.\n")
```

## Study {.tabset .tabset-pills}

### Buckets
```{r study-buckets, echo=FALSE, eval=has_premature}
Widget_PrematureDeathBucketBar(
  data = pd_BucketRows(dfClassified, nWindowDays, strGroupCol = "studyid"),
  spec = pd_BucketBarSpec(nWindowDays, "Study"),
  metadata = list(chartId = "pd-study-buckets", level = "study")
)
```

```{r study-buckets-note, echo=FALSE, results='asis', eval=has_premature}
cat(study_discont_note)
```

### Rand -> Death
```{r study-scatter, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-study-scatter",
  pd_RandToDeathScatter(dfScatter, nWindowDays, vXRange = vXRange, vYRange = vYRange)
)
```

```{r study-scatter-note, echo=FALSE, results='asis', eval=has_premature}
cat(study_discont_note)
```

### Reasons
```{r study-reasons, echo=FALSE, eval=has_premature}
Widget_PrematureDeathReasonBar(
  data = pd_ReasonRows(reason_data[["__ALL__"]]),
  # reason_order pins the study-wide count sort as a stable axis; the country
  # tab reuses the same order so its bar keeps position when a country is picked.
  spec = pd_ReasonBarSpec(reason_order = reason_data[["__ALL__"]]$reason),
  metadata = list(chartId = "pd-study-reasons", level = "study")
)
```

## Country {.tabset .tabset-pills}

### Buckets
```{r country-buckets, echo=FALSE, eval=has_premature}
Widget_PrematureDeathBucketBar(
  data = pd_BucketRows(dfClassified, nWindowDays, strGroupCol = "country"),
  # Country and site charts opt into zoom/pan (x-axis) — a multinational study
  # can carry many country bars; the single-bar study chart stays zoom-free.
  spec = pd_BucketBarSpec(nWindowDays, "Country", zoom = list(enabled = TRUE, mode = "x")),
  metadata = list(chartId = "pd-country-buckets", level = "country")
)
```

### Rand -> Death
```{r country-scatter, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-country-scatter",
  pd_RandToDeathScatter(dfScatter, nWindowDays, vXRange = vXRange, vYRange = vYRange)
)
```

### Reasons
```{r country-reasons, echo=FALSE, eval=has_premature}
# reactive: one row frame per country (+ __ALL__). A country bucket click
# broadcasts pdBucketFilterChanged, and the widget swaps to that slice via
# helpers.updateData — no per-country spec, no rebuildReasons.
reason_rows_by_country <- lapply(reason_data, pd_ReasonRows)
Widget_PrematureDeathReasonBar(
  data = reason_rows_by_country[["__ALL__"]],
  spec = pd_ReasonBarSpec(reason_order = reason_data[["__ALL__"]]$reason),
  metadata = list(
    chartId = "pd-country-reasons", level = "country",
    reactive = reason_rows_by_country
  )
)
```

## Site {.tabset .tabset-pills}

### Buckets
```{r site-buckets, echo=FALSE, eval=has_premature}
Widget_PrematureDeathBucketBar(
  # strOuterCol = "country" keeps each row's OuterGroupID so the country->site
  # drilldown can re-slice this chart to one country's sites (see filter-js).
  data = pd_BucketRows(dfClassified, nWindowDays, strGroupCol = "invid", strOuterCol = "country"),
  # Zoom/pan (x-axis): the site chart always renders every enrolled site (see
  # the country chart chunk for the shared rationale). dynamicCategoryAxis drops
  # a site off the axis once a disabled legend entry leaves it with nothing to
  # show, so hiding a death window thins the axis instead of leaving blank slots.
  spec = pd_BucketBarSpec(
    nWindowDays,
    "Site",
    zoom = list(enabled = TRUE, mode = "x"),
    theme = list(dynamicCategoryAxis = TRUE)
  ),
  metadata = list(chartId = "pd-site-buckets", level = "site")
)
```

### Rand -> Death
```{r site-scatter, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-site-scatter",
  pd_RandToDeathScatter(dfScatter, nWindowDays, vXRange = vXRange, vYRange = vYRange)
)
```

## Patient Listing
```{r patient-listing, echo=FALSE}
pd_PatientListing(dfResults, Mapped_Death, Mapped_SUBJ, Mapped_EXCLUSION, Mapped_AE)
```

```{r patient-listing-note, echo=FALSE, results='asis', eval=has_premature}
cat("\n> **Treatment Related** combines the death classification (`deathcls`) with adverse-event data: **Yes** when the death is classified as an adverse event *and* the subject has a fatal (CTCAE grade 5) treatment-related (`aerel` = `RELATED`) adverse event; **No** when either the death is classified as an adverse event *and* the subject has a fatal (grade 5) *not* treatment-related (`aerel` = `NOT RELATED`) adverse event, or the death is not classified as an adverse event *and* there is no fatal treatment-related adverse event; **Unknown** otherwise (e.g. an adverse-event death with no fatal adverse-event evidence, contradictory signals, or a missing death classification / adverse-event grade or relatedness). Note: the adverse event is matched by subject, not to the specific event that caused death.\n")
```

```{r eligibility-note, echo=FALSE, results='asis', eval=has_premature && has_eligibility}
cat(
  "\n",
  "> The Eligibility Status summarizes whether an enrolled participant met the study eligibility criteria, derived by combining data from the **IE** CRF  and **Protocol Deviations** reported in CTMS. It is determined as follows:\n",
  ">\n",
  "> - **Ineligible:** The participant triggered **at least one** of the eligibility signals. This applies whether they had an EDC I/E violation only, an eligibility protocol deviation only, or met both criteria.\n",
  "> - **Eligible:** The participant triggered **neither** of the eligibility signals (they have no EDC I/E violations and no eligibility-related protocol deviations).\n",
  "> - **Unknown:** The participant has no exclusion record available to evaluate.\n",
  sep = ""
)
```

```{r filter-js, echo=FALSE, results='asis', eval=has_premature}
cat(paste0('
<script>
(function() {
  var countrySiteMap = ', country_site_map, ';
  // activeCountry / activeSite are retained ONLY as mirrors of pdBucketState so
  // the kept scatter helpers (applySiteScatterFilter) keep working unchanged.
  var activeCountry = null;
  var activeSite = null;

  // ---- Retained Plotly scatter + listing helpers --------------------------
  // The scatter charts stay on Plotly (migration deferred with #120); these
  // helpers drive them and the DataTable off pdBucketState.

  // Find the plotly div inside a container (returns null until Plotly has
  // initialized the widget and attached its event system).
  function getPlotlyDiv(containerId) {
    var container = document.getElementById(containerId);
    if (!container) return null;
    var el = container.querySelector(".plotly");
    if (!el || !el.on) return null;
    return el;
  }

  // Show/hide the banner container based on whether either filter is active.
  function updateBannerVisibility() {
    var banner = document.getElementById("pd-filter-banner");
    banner.style.display = (pdBucketState.activeCountry || pdBucketState.activeSite) ? "flex" : "none";
  }

  // Single owner of the patient-listing column search. Only one search can be
  // held on the invid column, so both filters route through here. Precedence:
  // an active site wins over an active country (site is more specific).
  function applyListingFilter() {
    var tables = document.querySelectorAll(".dataTable");
    if (tables.length === 0) return;
    var dtApi = $(tables[tables.length - 1]).DataTable();
    var sites = null;
    if (pdBucketState.activeSite) {
      sites = [pdBucketState.activeSite];
    } else if (pdBucketState.activeCountry) {
      sites = countrySiteMap[pdBucketState.activeCountry] || [];
    }
    if (sites) {
      var regex = "^(" + sites.join("|") + ")$";
      dtApi.column("invid:name").search(regex, true, false).draw();
    } else {
      dtApi.column("invid:name").search("").draw();
    }
  }

  // Single owner of the site-scatter point filter. Same site > country > none
  // precedence as the listing: an active site shows just that site, else an
  // active country shows its sites, else all points return at the shared range.
  function applySiteScatterFilter() {
    if (activeSite) {
      filterScatterChart("pd-site-scatter", [activeSite], 2);
    } else if (activeCountry) {
      filterScatterChart("pd-site-scatter", countrySiteMap[activeCountry] || [], 2);
    } else {
      resetPlotlyChart("pd-site-scatter");
    }
  }

  // Cache each scatter clean trace data + layout the first time we touch it, so
  // a later reset can restore the un-filtered version. Idempotent.
  var originalData = {};
  var originalLayout = {};
  function cacheOriginal(el, containerId) {
    if (!originalData[containerId]) {
      originalData[containerId] = JSON.parse(JSON.stringify(el.data));
    }
    if (!originalLayout[containerId]) {
      originalLayout[containerId] = JSON.parse(JSON.stringify(el.layout));
    }
  }

  // Numeric-y scatters filter by per-point customdata: index 1 = country,
  // index 2 = invid. Reindex each trace x/y/customdata in lockstep, then react
  // with the CACHED layout so the fixed range is preserved (AXIS-1).
  function filterScatterChart(containerId, allowedValues, cdIndex) {
    var el = getPlotlyDiv(containerId);
    if (!el) return;
    cacheOriginal(el, containerId);
    var orig = originalData[containerId];
    var filtered = orig.map(function(trace) {
      if (!Array.isArray(trace.customdata)) return trace;
      var keep = [];
      trace.customdata.forEach(function(cd, idx) {
        if (cd && allowedValues.indexOf(cd[cdIndex]) >= 0) keep.push(idx);
      });
      var nt = Object.assign({}, trace);
      nt.x = keep.map(function(i) { return trace.x[i]; });
      nt.y = keep.map(function(i) { return trace.y[i]; });
      nt.customdata = keep.map(function(i) { return trace.customdata[i]; });
      return nt;
    });
    Plotly.react(el, filtered, JSON.parse(JSON.stringify(originalLayout[containerId])));
  }

  // Restore a scatter to its cached original (full point set, fixed range).
  // Scatter-only now: the bucket bars are gsm.viz canvases, not Plotly.
  function resetPlotlyChart(containerId) {
    var el = getPlotlyDiv(containerId);
    if (!el || !originalData[containerId]) return;
    Plotly.react(el, originalData[containerId], originalLayout[containerId] || el.layout);
  }

  // ---- gsm.viz bucket charts (#264) ---------------------------------------
  var PD_BUCKET_IDS = ["pd-study-buckets", "pd-country-buckets", "pd-site-buckets"];
  var pdBucketState = { activeCountry: null, activeSite: null };

  // Every bucket chart is a flat gsm.viz `bars` (a single Chart.js instance).
  function pdChartsFor(id) {
    var el = document.getElementById(id);
    return el && el.gsmChart ? [el.gsmChart] : [];
  }

  // Country->site drilldown: re-slice the site chart to the sites in the active
  // country (all sites when no country is active), reusing the rows the widget
  // kept on el.pdAllData. Runs before pdHighlightBuckets so a site highlight
  // lands on the freshly-swapped data.
  function pdNarrowSiteChart() {
    var el = document.getElementById("pd-site-buckets");
    if (!el || !el.gsmChart || !el.pdAllData) return;
    var country = pdBucketState.activeCountry;
    var rows = country
      ? el.pdAllData.filter(function(r) { return r.OuterGroupID === country; })
      : el.pdAllData;
    el.gsmChart.helpers.updateData(el.gsmChart, rows, el.gsmChart.data._spec_);
  }

  // Highlight the active group across the bucket charts. Single-owner
  // precedence: site > country > none. Only charts whose category axis actually
  // contains the selection are highlighted -- selectCategory with an absent
  // value dims every bar, which would grey out the study chart (categories are
  // studies, not countries/sites) or the country chart on a site selection.
  // Charts without a match clear instead, staying fully visible.
  function pdHighlightBuckets() {
    var sel = pdBucketState.activeSite || pdBucketState.activeCountry || null;
    PD_BUCKET_IDS.forEach(function(id) {
      pdChartsFor(id).forEach(function(c) {
        var labels = (c.data && c.data.labels) || [];
        if (sel && labels.indexOf(sel) >= 0) c.helpers.selectCategory(c, sel);
        else c.helpers.clearSelection(c);
      });
    });
  }

  // Reflect pdBucketState everywhere: mirror the scatter globals, update the
  // filter chips + banner, highlight the buckets, refilter the listing and the
  // two scatters (single-owner precedence), and broadcast pdBucketFilterChanged.
  function pdSyncBucketFilters() {
    activeCountry = pdBucketState.activeCountry;
    activeSite = pdBucketState.activeSite;

    // Show a chip and set its label when its filter value is active; hide otherwise.
    function setChip(chipId, valueId, value) {
      var chip = document.getElementById(chipId);
      if (value) {
        chip.style.display = "inline-flex";
        document.getElementById(valueId).textContent = value;
      } else {
        chip.style.display = "none";
      }
    }
    setChip("pd-filter-country-chip", "pd-filter-country-value", pdBucketState.activeCountry);
    setChip("pd-filter-site-chip", "pd-filter-site-value", pdBucketState.activeSite);
    updateBannerVisibility();
    pdNarrowSiteChart();
    pdHighlightBuckets();
    applyListingFilter();
    if (pdBucketState.activeCountry) {
      filterScatterChart("pd-country-scatter", [pdBucketState.activeCountry], 1);
    } else {
      resetPlotlyChart("pd-country-scatter");
    }
    applySiteScatterFilter();
    document.dispatchEvent(new CustomEvent("pdBucketFilterChanged", { bubbles: true,
      detail: { country: pdBucketState.activeCountry, invid: pdBucketState.activeSite } }));
  }

  // Bucket click handler: derive the new state from the clicked datum, then sync.
  // Clicking the bar that is already active toggles it off -- gsm.viz has a
  // deselect path of its own, but it is gated on spec.selection, which these
  // charts do not enable. Unlike a chip\'s reset button (which owns exactly one
  // filter), the country bar owns the drilldown, so toggling it off drops the
  // site with it.
  function pdApplyBucketFilter(detail) {
    if (detail.level === "country") {
      var country = detail.country || detail.groupId;
      pdBucketState.activeCountry = country === pdBucketState.activeCountry ? null : country;
      pdBucketState.activeSite = null;
    } else if (detail.level === "site") {
      var invid = detail.invid || detail.groupId;
      // The site is the leaf: toggling it off steps back to its country.
      if (invid === pdBucketState.activeSite) {
        pdBucketState.activeSite = null;
      } else {
        pdBucketState.activeSite = invid;
        pdBucketState.activeCountry = detail.country || pdBucketState.activeCountry;
      }
    }
    pdSyncBucketFilters();
  }

  // Chip reset buttons keep their inline onclick handlers (pdResetFilter /
  // pdResetSiteFilter). Clearing a country leaves any active site untouched and
  // vice-versa, matching the pre-migration single-owner behavior.
  window.pdResetFilter = function() {
    pdBucketState.activeCountry = null;
    pdSyncBucketFilters();
  };
  window.pdResetSiteFilter = function() {
    pdBucketState.activeSite = null;
    pdSyncBucketFilters();
  };

  document.addEventListener("pdBucketClick", function(e) { pdApplyBucketFilter(e.detail); });
})();
</script>
'))
```
