---
output:
  html_document:
    mathjax: null
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    css: styles.css
params:
  dfResults: NA
  dfMetrics: NA
  dfGroups: NA
  lListings: NA
  nWindowDays: 90
---

```{r setup, include=FALSE}
library(dplyr)
library(gsm.kri)
library(plotly)
library(DT)
library(htmltools)
library(knitr)
library(jsonlite)

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

dfResults <- params$dfResults
lListings <- params$lListings
nWindowDays <- params$nWindowDays

Mapped_Death <- lListings$Mapped_Death
Mapped_SUBJ <- lListings$Mapped_SUBJ
Mapped_STUDCOMP <- lListings$Mapped_STUDCOMP
Mapped_EXCLUSION <- lListings$Mapped_EXCLUSION
Mapped_AE <- lListings$Mapped_AE
Mapped_Randomization <- lListings$Mapped_Randomization

# In production Mapped_SUBJ has no randomization date; source it from
# Mapped_Randomization (passed in lListings). Then drop subjects with no
# randomization date -- they have no position on the randomization-anchored
# timeline, so they must not be counted in the bars yet dropped from the scatter.
if (!"rgmn_dt" %in% names(Mapped_SUBJ) && !is.null(Mapped_Randomization)) {
  Mapped_SUBJ <- dplyr::left_join(
    Mapped_SUBJ,
    dplyr::distinct(dplyr::select(Mapped_Randomization, "subjid", "rgmn_dt")),
    by = "subjid"
  )
}
if ("rgmn_dt" %in% names(Mapped_SUBJ)) {
  Mapped_SUBJ <- dplyr::filter(Mapped_SUBJ, !is.na(.data$rgmn_dt))
}

# Reporting snapshot drives follow-up (the two "alive" categories), so it is
# defined here, ahead of the single classification of every enrolled subject.
latest_snapshot <- max(dfResults$SnapshotDate)

# Single classification of every enrolled subject (the SOT for all charts).
dfClassified <- pd_Classify(
  dfSubjects = Mapped_SUBJ,
  dfDeath = Mapped_Death,
  dfStudComp = Mapped_STUDCOMP,
  nWindowDays = nWindowDays,
  dSnapshotDate = latest_snapshot
)

# Study-wide fixed scatter range, shared by the study/country/site views (AXIS-1).
# Derived from the data (not hardcoded); a 5% pad keeps boundary points off the edge.
x_max <- max(c(dfClassified$x_anchor, nWindowDays), na.rm = TRUE)
y_max <- max(c(dfClassified$follow_up, nWindowDays), na.rm = TRUE)
vXRange <- c(0, x_max * 1.05)
vYRange <- c(0, y_max * 1.05)

# Country → site lookup for JS filtering (all enrolled sites in the country)
country_site_map <- Mapped_SUBJ %>%
  dplyr::distinct(country, invid) %>%
  dplyr::group_by(country) %>%
  dplyr::summarise(sites = list(invid), .groups = "drop") %>%
  tibble::deframe() %>%
  jsonlite::toJSON(auto_unbox = FALSE)

# Reason counts split by country (+ "__ALL__"), serialized for the client-side
# rebuildReasons() handler. auto_unbox = FALSE keeps every field a JSON array so
# the JS .map() calls never hit a bare scalar for a single-reason country.
reason_by_country <- jsonlite::toJSON(
  pd_ReasonByCountry(Mapped_Death, Mapped_SUBJ, nWindowDays),
  auto_unbox = FALSE
)

has_eligibility <- !is.null(Mapped_EXCLUSION) && "Source" %in% names(Mapped_EXCLUSION)

# Overview summary numbers, computed once from the classified cohort (the single
# source of truth). Driving nEnrolled / nPremature from here -- not a separate
# pd_PrematureCohort count -- means the Overview table, the empty-state, every
# chart's eval=has_premature gate, and the window-consistency guard below all
# describe the one cohort the bucket bars and scatter render, so they can never
# drift apart (a duplicate death row or a death for an unmapped subject no longer
# makes the guard and the table disagree).
stats <- pd_OverviewStats(dfClassified, Mapped_EXCLUSION, nWindowDays)
nEnrolled <- stats$nEnrolled
nPremature <- stats$nPremature
nPrematureRate <- stats$nPrematureRate
has_premature <- nPremature > 0

# Study-discontinuation caveat, shared verbatim by the Study Buckets and the
# Study Rand -> Death tabs (single source of truth so the embedded nWindowDays
# can't drift between the two placements).
study_discont_note <- paste0(
  "\n> **Study discontinuation** is taken from study-completion records (`studcomp`): a subject is counted here when their record indicates discontinuation within ",
  nWindowDays,
  " days of randomization for a reason other than death. Deaths within ",
  nWindowDays,
  " days appear under *Death within ",
  nWindowDays,
  " days*; subjects still on study appear under the *Alive* categories. Discontinuation timing is approximated from the study-completion record date.\n"
)

# Consistency guard: the charts recompute premature status from Mapped_Death at
# nWindowDays; the patient listing trusts pat0015 Flag==2 rows (flagged at
# analysis-time meta.WindowDays). A divergence means nWindowDays != the window
# that produced dfResults -> charts and listing describe different windows.
nFlagged <- sum(
  dfResults$MetricID == "Analysis_pat0015" & dfResults$Flag == 2,
  na.rm = TRUE
)
if (nFlagged != nPremature) {
  pd_CheckWindowConsistency(nWindowDays, nPremature, nFlagged)
}
```

---
title: "Premature Deaths Overview"
subtitle: "Study: `r unique(Mapped_SUBJ$studyid)`"
date: "Snapshot Date: `r latest_snapshot`"
---

# Premature Deaths Overview

```{r filter-strip-css, echo=FALSE, results='asis'}
# The chip strip's styling ships as an inline <style> block HERE, not via
# styles.css, so it survives every host context. The standalone report links
# styles.css, but the pkgdown example embeds this report through knit_child and
# does NOT load styles.css -- there the chips would render unstyled and
# non-sticky. Literal hex (no var(--...) tokens) for the same reason: the :root
# tokens defined in styles.css aren't present in the embedded context. Same
# inline-<style> pattern the rangeslider-css chunk below uses.
cat('
<style>
.pd-filter-strip { position: sticky; top: 0; z-index: 1030; display: none; align-items: center; flex-wrap: wrap; gap: 10px; background-color: #f1f7fe; border-bottom: 1px solid #cfe3fb; padding: 8px 14px; margin: 0 0 16px; }
.pd-filter-eyebrow { font-size: 11px; font-weight: 600; letter-spacing: 0.08em; text-transform: uppercase; color: #5b7193; }
.pd-filter-chip { display: inline-flex; align-items: center; gap: 6px; background-color: #ffffff; border: 1px solid #3C587F; border-radius: 16px; padding: 3px 6px 3px 12px; font-size: 13px; color: #3C587F; }
.pd-chip-value { font-weight: 600; }
.pd-filter-chip button { display: inline-flex; align-items: center; justify-content: center; width: 18px; height: 18px; padding: 0; border: none; border-radius: 50%; background-color: transparent; color: #3C587F; font-size: 13px; line-height: 1; cursor: pointer; }
.pd-filter-chip button:hover { background-color: #3C587F; color: #ffffff; }
.pd-filter-chip button:focus-visible { outline: 2px solid #3C587F; outline-offset: 2px; }
</style>
')
```

```{r filter-strip, echo=FALSE}
# Sticky cross-filter strip: one chip per active country/site filter, shown by
# the filter-js chunk as selections change. Built with htmltools (not raw HTML)
# so pandoc doesn't wrap the inline chips in a <p>, which would break the flex
# row and add stray paragraph margins. Hidden (CSS display:none) until a filter
# is active.
htmltools::tags$div(
  id = "pd-filter-banner", class = "pd-filter-strip",
  htmltools::tags$span(class = "pd-filter-eyebrow", "Filtering"),
  htmltools::tags$span(
    id = "pd-filter-country-chip", class = "pd-filter-chip", style = "display:none;",
    htmltools::tags$span(
      class = "pd-chip-label", "Country: ",
      htmltools::tags$span(id = "pd-filter-country-value", class = "pd-chip-value")
    ),
    htmltools::tags$button(
      id = "pd-filter-reset", onclick = "pdResetFilter()",
      `aria-label` = "Clear country filter", htmltools::HTML("&times;")
    )
  ),
  htmltools::tags$span(
    id = "pd-filter-site-chip", class = "pd-filter-chip", style = "display:none;",
    htmltools::tags$span(
      class = "pd-chip-label", "Site: ",
      htmltools::tags$span(id = "pd-filter-site-value", class = "pd-chip-value")
    ),
    htmltools::tags$button(
      id = "pd-site-filter-reset", onclick = "pdResetSiteFilter()",
      `aria-label` = "Clear site filter", htmltools::HTML("&times;")
    )
  )
)
```

## Overview

Premature death analysis supports early identification of deaths occurring within ≤`r nWindowDays` days of randomization, enabling timely detection of potential eligibility concerns and emerging safety risks.

```{r overview-table, echo=FALSE}
# Ineligible needs eligibility data (Mapped_EXCLUSION); when it is absent we show
# a dash rather than 0, which would falsely assert zero ineligible deaths.
ineligible_cell <- if (stats$has_eligibility) {
  sprintf("%d (%.1f%%)", stats$nIneligible, stats$nIneligibleRate)
} else {
  "—"
}
knitr::kable(
  data.frame(
    "Total enrolled" = stats$nEnrolled,
    "Total sites with enrolled participants" = stats$nSites,
    "Premature Death(s)" = sprintf("%d (%.1f%%)", stats$nPremature, stats$nPrematureRate),
    "Ineligible Premature Death(s)" = ineligible_cell,
    check.names = FALSE
  ),
  format = "html",
  align = "r",
  table.attr = "class=\"table\""
)
```

```{r empty-state, echo=FALSE, results='asis', eval=!has_premature}
cat("\n> **No premature deaths in window.** All charts and the patient listing are empty for this snapshot.\n")
```

```{r mode-toggle, echo=FALSE, results='asis', eval=has_premature}
cat('
<div id="pd-mode-toggle" style="margin:12px 0;">
  <span style="font-size:13px; color:#555; margin-right:8px;">Bucket bars:</span>
  <button id="pd-mode-count" onclick="pdSetMode(\'count\')" style="background:#1a73e8; color:white; border:none; border-radius:4px; padding:4px 14px; cursor:pointer; font-size:12px;">Count</button>
  <button id="pd-mode-pct" onclick="pdSetMode(\'pct\')" style="background:#cfd8dc; color:#37474f; border:none; border-radius:4px; padding:4px 14px; cursor:pointer; font-size:12px;">%</button>
</div>
')
```

```{r rangeslider-css, echo=FALSE, results='asis', eval=has_premature}
# Hide each bucket bar's range-slider mini-preview, leaving a scroll-only track,
# and recolor its grabber handles. Plotly draws the handles white (fill="#fff"),
# which is invisible on the grey track styled in pd_BucketBar(); a fill of #828282
# (colorScheme gray/dark) makes them read as grips. CSS fill overrides Plotly's
# presentation attribute. Scoped to the three bucket-bar container ids so it never
# reaches another gsm.kri report sharing styles.css; a stylesheet rule (not inline
# JS) re-matches the slider DOM that Plotly.react rebuilds on every filter.
cat('
<style>
#pd-study-buckets .rangeslider-rangeplot,
#pd-country-buckets .rangeslider-rangeplot,
#pd-site-buckets .rangeslider-rangeplot { display: none !important; }
#pd-study-buckets .rangeslider-handle-min, #pd-study-buckets .rangeslider-handle-max,
#pd-country-buckets .rangeslider-handle-min, #pd-country-buckets .rangeslider-handle-max,
#pd-site-buckets .rangeslider-handle-min, #pd-site-buckets .rangeslider-handle-max { fill: #828282 !important; }
</style>
')
```

## Study {.tabset .tabset-pills}

### Buckets
```{r study-buckets, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-study-buckets",
  pd_BucketBar(dfClassified, nWindowDays, strGroupCol = "studyid", strGroupLabel = "Study", bRangeSlider = TRUE)
)
```

```{r study-buckets-note, echo=FALSE, results='asis', eval=has_premature}
cat(study_discont_note)
```

### Rand -> Death
```{r study-scatter, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-study-scatter",
  pd_RandToDeathScatter(dfClassified, nWindowDays, vXRange = vXRange, vYRange = vYRange)
)
```

```{r study-scatter-note, echo=FALSE, results='asis', eval=has_premature}
cat(study_discont_note)
```

### Reasons
```{r study-reasons, echo=FALSE, eval=has_premature}
pd_ReasonDist(Mapped_Death, nWindowDays, nEnrolled = nEnrolled)
```

## Country {.tabset .tabset-pills}

### Buckets
```{r country-buckets, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-country-buckets",
  pd_BucketBar(dfClassified, nWindowDays, strGroupCol = "country", strGroupLabel = "Country", strOuterCol = "studyid", bRangeSlider = TRUE)
)
```

### Rand -> Death
```{r country-scatter, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-country-scatter",
  pd_RandToDeathScatter(dfClassified, nWindowDays, vXRange = vXRange, vYRange = vYRange)
)
```

### Reasons
```{r country-reasons, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-country-reasons",
  pd_ReasonDist(Mapped_Death, nWindowDays)
)
```

## Site {.tabset .tabset-pills}

### Buckets
```{r site-buckets, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-site-buckets",
  pd_BucketBar(dfClassified, nWindowDays, strGroupCol = "invid", strGroupLabel = "Site", strOuterCol = "country", strOuterLabel = "Country", bRangeSlider = TRUE)
)
```

### Rand -> Death
```{r site-scatter, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-site-scatter",
  pd_RandToDeathScatter(dfClassified, nWindowDays, vXRange = vXRange, vYRange = vYRange)
)
```

## Patient Listing
```{r patient-listing, echo=FALSE}
pd_PatientListing(dfResults, Mapped_Death, Mapped_SUBJ, Mapped_EXCLUSION, Mapped_AE)
```

```{r patient-listing-note, echo=FALSE, results='asis', eval=has_premature}
cat("\n> **Treatment Related** combines the death classification (`deathcls`) with adverse-event data: **Yes** when the death is classified as an adverse event *and* the subject has a fatal (CTCAE grade 5) treatment-related (`aerel` = `RELATED`) adverse event; **No** when either the death is classified as an adverse event *and* the subject has a fatal (grade 5) *not* treatment-related (`aerel` = `NOT RELATED`) adverse event, or the death is not classified as an adverse event *and* there is no fatal treatment-related adverse event; **Unknown** otherwise (e.g. an adverse-event death with no fatal adverse-event evidence, contradictory signals, or a missing death classification / adverse-event grade or relatedness). Note: the adverse event is matched by subject, not to the specific event that caused death.\n")
```

```{r eligibility-note, echo=FALSE, results='asis', eval=has_premature && has_eligibility}
cat("\n> **Eligibility Status** is derived from `Mapped_EXCLUSION`: **Ineligible** when an inclusion/exclusion or eligibility protocol-deviation violation is recorded (`Source` != `Neither`); **Eligible** when none is recorded (`Source` == `Neither`); **Unknown** when the subject has no eligibility record.\n")
```

```{r filter-js, echo=FALSE, results='asis', eval=has_premature}
cat(paste0('
<script>
(function() {
  var countrySiteMap = ', country_site_map, ';
  var reasonByCountry = ', reason_by_country, ';
  var activeCountry = null;
  var activeSite = null;

  // Find the plotly div inside a container (returns null until Plotly has
  // initialized the widget and attached its event system).
  function getPlotlyDiv(containerId) {
    var container = document.getElementById(containerId);
    if (!container) return null;
    var el = container.querySelector(".plotly");
    if (!el || !el.on) return null;
    return el;
  }

  // The interactive charts carry their category dimension as a 2-D
  // multicategory axis [[outer],[inner]] -- bars on x, scatters on y. This
  // returns the inner tier (the site / country labels) regardless of which axis
  // holds it, so the helpers below never branch on chart shape.
  function catLabels(tr) {
    if (Array.isArray(tr.x) && Array.isArray(tr.x[0])) return tr.x[1];
    if (Array.isArray(tr.y) && Array.isArray(tr.y[0])) return tr.y[1];
    return tr.x; // flat fallback (defensive; interactive charts are 2-D)
  }

  // Restore every bar in a chart to full opacity (one batched restyle).
  function undimBars(containerId) {
    var el = getPlotlyDiv(containerId);
    if (!el) return;
    var opacities = el.data.map(function(tr) {
      return catLabels(tr).map(function() { return 1.0; });
    });
    Plotly.restyle(el, {"marker.opacity": opacities}, el.data.map(function(_, i) { return i; }));
  }

  // Dim every bar except those whose category equals `value` (one batched
  // restyle across all traces).
  function dimBarsExcept(el, value) {
    var opacities = el.data.map(function(tr) {
      return catLabels(tr).map(function(v) { return v === value ? 1.0 : 0.3; });
    });
    Plotly.restyle(el, {"marker.opacity": opacities}, el.data.map(function(_, i) { return i; }));
  }

  // Attach click handler to country buckets chart (retry until Plotly ready, max 20)
  var attachRetries = 0;
  function attachCountryClick() {
    var el = getPlotlyDiv("pd-country-buckets");
    if (!el) {
      if (++attachRetries < 20) setTimeout(attachCountryClick, 500);
      return;
    }
    el.on("plotly_click", function(data) {
      var country = data.points[0].x[1]; // multicategory click -> [study, country]
      if (country === activeCountry) {
        pdResetFilter();
      } else {
        applyFilter(country);
      }
    });
  }

  function applyFilter(country) {
    activeCountry = country;
    var sites = countrySiteMap[country] || [];

    // Show the country chip naming the active country.
    document.getElementById("pd-filter-country-chip").style.display = "inline-flex";
    document.getElementById("pd-filter-country-value").textContent = country;
    updateBannerVisibility();

    // Highlight country bar: dim non-selected
    highlightCountryBar(country);

    // Country scatter: keep points in the selected country (customdata[1]).
    filterScatterChart("pd-country-scatter", [country], 1);

    // Site scatter: single owner applies site > country precedence (a site
    // selection, if any, stays narrowed; otherwise the country sites show).
    applySiteScatterFilter();

    // Site buckets are still multicategory -> existing bar filter.
    filterPlotlyChart("pd-site-buckets", sites);

    // The site-buckets re-render above wiped any site-bar opacity highlight;
    // re-apply it so an active, independent site selection stays visible.
    if (activeSite) highlightSiteBar(activeSite);

    // Re-derive the listing from all active filters (site > country precedence).
    applyListingFilter();
    rebuildReasons(country);
  }

  function highlightCountryBar(country) {
    var el = getPlotlyDiv("pd-country-buckets");
    if (!el) return;
    dimBarsExcept(el, country);
  }

  // Show/hide the banner container based on whether either row is active.
  function updateBannerVisibility() {
    var banner = document.getElementById("pd-filter-banner");
    banner.style.display = (activeCountry || activeSite) ? "flex" : "none";
  }

  // Single owner of the patient-listing column search. Only one search can be
  // held on the invid column, so both filters route through here. Precedence:
  // an active site wins over an active country (site is more specific).
  function applyListingFilter() {
    var tables = document.querySelectorAll(".dataTable");
    if (tables.length === 0) return;
    var dtApi = $(tables[tables.length - 1]).DataTable();
    var sites = null;
    if (activeSite) {
      sites = [activeSite];
    } else if (activeCountry) {
      sites = countrySiteMap[activeCountry] || [];
    }
    if (sites) {
      var regex = "^(" + sites.join("|") + ")$";
      dtApi.column("invid:name").search(regex, true, false).draw();
    } else {
      dtApi.column("invid:name").search("").draw();
    }
  }

  // Single owner of the site-scatter point filter (the scatter has the same two
  // filter sources as the listing). Same site > country > none precedence: an
  // active site shows just that site, else an active country shows its sites,
  // else all points return at the shared fixed range. Routing every caller
  // through here keeps the scatter and listing in lockstep.
  function applySiteScatterFilter() {
    if (activeSite) {
      filterScatterChart("pd-site-scatter", [activeSite], 2);
    } else if (activeCountry) {
      filterScatterChart("pd-site-scatter", countrySiteMap[activeCountry] || [], 2);
    } else {
      resetPlotlyChart("pd-site-scatter");
    }
  }

  // Attach click handler to site buckets chart (retry until Plotly ready, max 20)
  var siteAttachRetries = 0;
  function attachSiteClick() {
    var el = getPlotlyDiv("pd-site-buckets");
    if (!el) {
      if (++siteAttachRetries < 20) setTimeout(attachSiteClick, 500);
      return;
    }
    el.on("plotly_click", function(data) {
      var invid = data.points[0].x[1]; // multicategory click -> [country, site]
      if (invid === activeSite) {
        pdResetSiteFilter();
      } else {
        applySiteFilter(invid);
      }
    });
  }

  function applySiteFilter(invid) {
    activeSite = invid;
    document.getElementById("pd-filter-site-chip").style.display = "inline-flex";
    document.getElementById("pd-filter-site-value").textContent = invid;
    updateBannerVisibility();
    highlightSiteBar(invid);
    // Narrow the site scatter to just this site (single owner, customdata[2]).
    applySiteScatterFilter();
    applyListingFilter();
  }

  function highlightSiteBar(invid) {
    var el = getPlotlyDiv("pd-site-buckets");
    if (!el) return;
    // Seed the filter cache with CLEAN (un-dimmed) data BEFORE dimming below.
    // pd-site-buckets is the one chart that is both a highlight target and a
    // filter target: if a site is clicked before any country filter,
    // filterPlotlyChart would otherwise lazily cache this dimmed chart as the
    // "original", and a later country reset would restore a permanently-dimmed
    // chart. cacheOriginal is idempotent, so a clean cache (seeded here on a
    // site-first click, or by filterPlotlyChart on a country-first click) is
    // never overwritten.
    cacheOriginal(el, "pd-site-buckets");
    // If the selected site isn\'t currently rendered (e.g. a country filter is
    // showing a different country\'s sites), leave opacities untouched rather
    // than dimming every bar to 0.3.
    var present = el.data.some(function(tr) { return catLabels(tr).indexOf(invid) >= 0; });
    if (!present) return;
    dimBarsExcept(el, invid);
  }

  // Global reset for the site filter (called by the site row\'s button onclick)
  window.pdResetSiteFilter = function() {
    activeSite = null;
    document.getElementById("pd-filter-site-chip").style.display = "none";
    updateBannerVisibility();

    // Un-dim site bars
    undimBars("pd-site-buckets");

    // The site click narrowed the site scatter; restore it from the remaining
    // state (the active country\'s sites, or all points) via the single owner.
    applySiteScatterFilter();

    // Re-derive the listing from any remaining active filter (e.g. country).
    applyListingFilter();
  };

  // Store original trace data + layout for each chart on first filter
  var originalData = {};
  var originalLayout = {};

  // Cache a chart\'s clean trace data + layout the first time we touch it, so a
  // later reset can restore the un-filtered, un-dimmed version. Idempotent: a
  // second call never overwrites an existing (clean) cache.
  function cacheOriginal(el, containerId) {
    if (!originalData[containerId]) {
      originalData[containerId] = JSON.parse(JSON.stringify(el.data));
    }
    if (!originalLayout[containerId]) {
      originalLayout[containerId] = JSON.parse(JSON.stringify(el.layout));
    }
  }

  function filterPlotlyChart(containerId, allowedValues) {
    var el = getPlotlyDiv(containerId);
    if (!el) return;
    cacheOriginal(el, containerId);
    var orig = originalData[containerId];
    var filtered = orig.map(function(trace) {
      // The multicategory axis is the one whose first entry is itself an array
      // ([[outer],[inner]]); its inner tier holds the labels we filter on. Bars
      // carry it on x, scatters on y.
      var axis = (Array.isArray(trace.x) && Array.isArray(trace.x[0])) ? "x"
               : (Array.isArray(trace.y) && Array.isArray(trace.y[0])) ? "y"
               : null;
      if (!axis) return trace;
      var inner = trace[axis][1];
      var indices = [];
      inner.forEach(function(val, idx) {
        if (allowedValues.indexOf(val) >= 0) indices.push(idx);
      });
      var valueAxis = axis === "x" ? "y" : "x";
      var newTrace = Object.assign({}, trace);
      // One `indices` list reindexes every per-point array in lockstep: both
      // tiers of the category axis, the numeric value axis, and customdata --
      // index i addresses the same data point in all of them.
      newTrace[axis] = [
        indices.map(function(i) { return trace[axis][0][i]; }),
        indices.map(function(i) { return trace[axis][1][i]; })
      ];
      if (trace[valueAxis]) {
        newTrace[valueAxis] = indices.map(function(i) { return trace[valueAxis][i]; });
      }
      if (trace.text) newTrace.text = indices.map(function(i) { return trace.text[i]; });
      if (trace.customdata) newTrace.customdata = indices.map(function(i) { return trace.customdata[i]; });
      return newTrace;
    });
    // A reindexed multicategory axis re-derives its own ticks from the data, so
    // the empty-slot workaround the flat axis needed is gone. Clone the cached
    // layout so Plotly.react cannot mutate the stored original.
    Plotly.react(el, filtered, JSON.parse(JSON.stringify(originalLayout[containerId])));
    // Only the bucket bars carry [count, pct]; scatters pack a hover string in
    // customdata, so applyMode() must never run on them (it would garble y / the
    // axis). PD_BUCKET_CHARTS already lists exactly the three bucket containers.
    // Unconditional (not just % mode): restyle mutates el.data in place, so a
    // cache seeded while % mode was active holds % y values; re-deriving y from
    // customdata on every react makes that polluted cache harmless in both modes.
    if (PD_BUCKET_CHARTS.indexOf(containerId) >= 0) applyMode(el);
  }

  // Country-reactive reasons bar. Not a bucket chart and not a scatter, so it is
  // rebuilt from the precomputed per-country lookup (counts are aggregated, so a
  // point-reindex like the other charts cannot apply). null -> the all-country
  // aggregate, which restores the initial paint.
  function rebuildReasons(country) {
    var el = getPlotlyDiv("pd-country-reasons");
    if (!el) return;
    var d = reasonByCountry[country || "__ALL__"] || {reason: [], n: [], hover: []};
    Plotly.react(el, [{
      type: "bar", orientation: "h",
      x: d.n, y: d.reason,
      text: d.n, textposition: "auto",
      customdata: d.hover,
      hovertemplate: "%{customdata}<extra></extra>"
      // F1: no marker.color -- omitting it uses plotly\'s default colorway[0],
      // the same color the server-rendered pd_ReasonDist() draws, so the
      // all-country bar is identical before any interaction and after a
      // filter -> clear cycle.
    }], {
      xaxis: {title: "Premature Deaths"},
      yaxis: {title: "Reason", categoryorder: "total ascending"}
    });
  }

  // Numeric-y scatters filter by per-point customdata: index 1 = country,
  // index 2 = invid. Reindex each trace\'s x/y/customdata in lockstep, then
  // react with the CACHED layout so the fixed [x]/[y] range is preserved
  // (no autorange to the filtered subset -- AXIS-1).
  function filterScatterChart(containerId, allowedValues, cdIndex) {
    var el = getPlotlyDiv(containerId);
    if (!el) return;
    cacheOriginal(el, containerId);
    var orig = originalData[containerId];
    var filtered = orig.map(function(trace) {
      if (!Array.isArray(trace.customdata)) return trace;
      var keep = [];
      trace.customdata.forEach(function(cd, idx) {
        if (cd && allowedValues.indexOf(cd[cdIndex]) >= 0) keep.push(idx);
      });
      var nt = Object.assign({}, trace);
      nt.x = keep.map(function(i) { return trace.x[i]; });
      nt.y = keep.map(function(i) { return trace.y[i]; });
      nt.customdata = keep.map(function(i) { return trace.customdata[i]; });
      return nt;
    });
    Plotly.react(el, filtered, JSON.parse(JSON.stringify(originalLayout[containerId])));
  }

  // Global reset for the country filter (called by the country row\'s button onclick)
  window.pdResetFilter = function() {
    activeCountry = null;

    // Hide the country chip (the site chip stays as-is)
    document.getElementById("pd-filter-country-chip").style.display = "none";
    updateBannerVisibility();

    // Reset country bar opacity
    undimBars("pd-country-buckets");

    // Reset charts the country filter owns
    resetPlotlyChart("pd-country-scatter");
    resetPlotlyChart("pd-site-buckets");
    // Site scatter via the single owner so a still-active site stays narrowed
    // (else it returns to all points at the shared fixed range).
    applySiteScatterFilter();

    // The site-buckets reset above wiped any site-bar highlight; re-apply it
    // if a site filter is still active.
    if (activeSite) highlightSiteBar(activeSite);

    // Re-derive the listing from any remaining active filter (keeps a site).
    applyListingFilter();
    rebuildReasons(null);
  };

  function resetPlotlyChart(containerId) {
    var el = getPlotlyDiv(containerId);
    if (!el || !originalData[containerId]) return;
    // Restore the original layout so the full categorical axis returns
    Plotly.react(el, originalData[containerId], originalLayout[containerId] || el.layout);
    // Bucket charts only -- see the filterPlotlyChart note: scatters are filter
    // targets too, and applyMode() would corrupt their string customdata / y-axis.
    // Unconditional for the same reason as filterPlotlyChart: the cached
    // "original" may carry %-mode y values; applyMode re-derives the right y
    // for the CURRENT mode from customdata either way.
    if (PD_BUCKET_CHARTS.indexOf(containerId) >= 0) applyMode(el);
  }

  // ---- Count <-> % toggle for the three bucket bars -----------------------
  // pd_BucketBar packs [count, pct] per point into customdata; y is always
  // re-derived from it, so the mode is stateless and survives the Plotly.react
  // the filters trigger (re-applied at the tail of every react below).
  var pdMode = "count";
  var PD_BUCKET_CHARTS = ["pd-study-buckets", "pd-country-buckets", "pd-site-buckets"];

  function applyMode(el) {
    if (!el || !el.data) return;
    var slot = pdMode === "pct" ? 1 : 0;
    var traceIndices = el.data.map(function(_, idx) { return idx; });
    var ys = el.data.map(function(tr) {
      return (tr.customdata || []).map(function(cd) { return cd[slot]; });
    });
    // On-bar labels track the mode: the count in count mode, the rounded % in %
    // mode; an empty bucket (count 0) stays blank either way. customdata is
    // [count, pct] per point, so the label is re-derived alongside y.
    var texts = el.data.map(function(tr) {
      return (tr.customdata || []).map(function(cd) {
        if (!cd[0]) return "";
        return pdMode === "pct" ? Math.round(cd[1]) + "%" : String(cd[0]);
      });
    });
    // One atomic data+layout update (single redraw) instead of restyle+relayout
    // avoids the bars-resized-but-axis-stale flicker frame on every react. BOTH
    // modes autorange (range:null) so hiding a category via the legend rescales
    // the y-axis to the remaining traces -- count to the remaining total, % to
    // the remaining stacked share. Pinning % to [0,100] would freeze that rescale.
    var layoutUpdate = pdMode === "pct"
      ? {"yaxis.title.text": "% of group", "yaxis.ticksuffix": "%", "yaxis.autorange": true, "yaxis.range": null}
      : {"yaxis.title.text": "Subjects", "yaxis.ticksuffix": "", "yaxis.autorange": true, "yaxis.range": null};
    Plotly.update(el, {y: ys, text: texts}, layoutUpdate, traceIndices);
  }

  window.pdSetMode = function(mode) {
    pdMode = mode;
    // Flip text color WITH background: white text on the inactive light-grey
    // (#cfd8dc) would be illegible, so the inactive side gets dark text.
    var btnCount = document.getElementById("pd-mode-count");
    var btnPct = document.getElementById("pd-mode-pct");
    btnCount.style.background = mode === "count" ? "#1a73e8" : "#cfd8dc";
    btnCount.style.color = mode === "count" ? "white" : "#37474f";
    btnPct.style.background = mode === "pct" ? "#1a73e8" : "#cfd8dc";
    btnPct.style.color = mode === "pct" ? "white" : "#37474f";
    PD_BUCKET_CHARTS.forEach(function(id) { applyMode(getPlotlyDiv(id)); });
  };

  // Initialize when DOM is ready
  function attachClickHandlers() {
    attachCountryClick();
    attachSiteClick();
  }
  if (document.readyState === "complete") {
    attachClickHandlers();
  } else {
    window.addEventListener("load", attachClickHandlers);
  }
})();
</script>
'))
```
