---
output:
  html_document:
    mathjax: null
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    css: styles.css
params:
  dfAE: NA
  dfSubj: NA
  strStudyID: "Study"
  dfFlagged: NA
  nMinAE: 20
  nTopTerms: 10
  nMinTermStudy: 50
  nMinTermSite: 10
  nDiffThreshold: 0.20
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.retina = 2
)
library(dplyr)
library(ggplot2)
library(gt)
```

```{r compute}
dfDist <- AEGrading_SiteDistribution(
  params$dfAE,
  params$dfSubj,
  nMinAE = params$nMinAE
)

dfTerm <- AEGrading_TermConsistency(
  params$dfAE,
  params$dfSubj,
  nTopTerms = params$nTopTerms,
  nMinTermStudy = params$nMinTermStudy,
  nMinTermSite = params$nMinTermSite,
  nDiffThreshold = params$nDiffThreshold
)

dfSiteTerm <- AEGrading_SiteTermSummary(dfTerm)

nSites <- dplyr::n_distinct(dfDist$GroupID)
nAE <- sum(dfDist$Count)
dfStudyGrade <- dfDist %>%
  dplyr::distinct(Grade, StudyProportion) %>%
  dplyr::arrange(Grade)
nStudyHigh <- sum(dfStudyGrade$StudyProportion[dfStudyGrade$Grade >= 3])
```

# AE Grading Overview {.tabset}

**Study:** `r params$strStudyID`
**Report generated:** `r format(Sys.Date(), "%d %B %Y")`

This report examines how consistently investigator sites apply CTCAE severity
grading to adverse events. It is a companion to the two site-level grading KRIs
(`kri0016` High-Grade AE Proportion and `kri0017` Low-Grade AE Proportion) and adds
the term-level detail those aggregate metrics cannot show.

It looks at grading from two angles:

1. **Overall severity mix** — does a site's distribution of Grade 1–5 events look
   like the rest of the study? This catches sites that grade nearly everything as
   Grade 1, or nearly everything as Grade 3/4.
2. **Term-level consistency** — for the most commonly reported preferred terms,
   does the site grade *the same event* the way the rest of the study does? This
   catches sites whose overall mix looks unremarkable but who apply the criteria
   inconsistently from one term to the next.

`r nAE` graded adverse events across `r nSites` sites met the minimum volume
threshold of `r params$nMinAE` graded AEs per site. Study-wide,
**`r sprintf("%.1f%%", nStudyHigh * 100)`** of adverse events are Grade 3 or higher.

## Study-wide grade distribution

```{r study-dist}
dfStudyGrade %>%
  dplyr::mutate(
    Grade = paste("Grade", Grade),
    Events = round(StudyProportion * nAE),
    StudyProportion = scales::percent(StudyProportion, accuracy = 0.1)
  ) %>%
  dplyr::select(Grade, Events, `% of all AEs` = StudyProportion) %>%
  gt::gt() %>%
  gt::tab_options(table.width = gt::pct(60))
```

# Grade distribution by site

Each bar is one site's severity mix, sorted by the proportion of Grade 3+ events.
Sites at the top report the highest share of severe events; sites at the bottom
report the lowest. The dashed line marks the study-wide Grade 3+ proportion —
bars that break well away from it in either direction are the sites whose grading
behaviour differs from their peers.

```{r grade-by-site, fig.width = 10, fig.height = 12}
Visualize_GradeBySite(
  dfDist,
  dfFlagged = if (is.data.frame(params$dfFlagged)) params$dfFlagged else NULL
)
```

```{r flagged-sites, results = "asis"}
if (is.data.frame(params$dfFlagged) && nrow(params$dfFlagged) > 0) {
  dfF <- params$dfFlagged %>%
    dplyr::filter(!is.na(Flag), Flag != 0) %>%
    dplyr::arrange(desc(abs(Score)))

  cat("\n## Sites flagged by the grading KRI\n\n")

  if (nrow(dfF) == 0) {
    cat("No sites were flagged.\n")
  } else {
    dfF %>%
      dplyr::transmute(
        Site = GroupID,
        `Grade 3+ events` = Numerator,
        `Total AEs` = Denominator,
        `Site %` = scales::percent(Metric, accuracy = 0.1),
        `Study %` = scales::percent(OverallMetric, accuracy = 0.1),
        `Z-score` = round(Score, 2),
        Flag = ifelse(Flag > 0, "Over-grading", "Under-grading")
      ) %>%
      gt::gt() %>%
      gt::tab_options(table.width = gt::pct(100)) %>%
      print()
  }
}
```

# Term-level grading consistency

The overall severity mix is a blunt instrument: a site can report a perfectly
average proportion of severe events while still grading individual event types
inconsistently. This section compares each site against the study for the
`r params$nTopTerms` most frequently reported preferred terms, so a site's case
mix cannot be mistaken for a grading difference.

**Evaluation rules**

- A preferred term is evaluated if it has at least `r params$nMinTermStudy` events study-wide.
- A site is evaluated on that term if it reported at least `r params$nMinTermSite` events of it.
- A site/term pair is flagged when its Grade 3+ proportion differs from the
  study-wide proportion for that term by at least
  `r scales::percent(params$nDiffThreshold)` (in either direction).
- A site is raised for investigation when it is flagged on **two or more** terms.

```{r term-counts}
dfTerm %>%
  dplyr::distinct(Term, StudyN, StudyHighGrade) %>%
  dplyr::arrange(desc(StudyN)) %>%
  dplyr::transmute(
    `Preferred term` = Term,
    `Events (study)` = StudyN,
    `Grade 3+ (study)` = scales::percent(StudyHighGrade, accuracy = 0.1)
  ) %>%
  gt::gt() %>%
  gt::tab_header(title = "Preferred terms evaluated") %>%
  gt::tab_options(table.width = gt::pct(70))
```

## Site-by-term deviation

```{r heatmap, fig.width = 10, fig.height = 8}
Visualize_TermGradingHeatmap(dfTerm)
```

## Sites to investigate

```{r investigate}
dfInv <- dfSiteTerm %>% dplyr::filter(Investigate)

if (nrow(dfInv) == 0) {
  cat("No sites were flagged on two or more preferred terms.")
} else {
  dfInv %>%
    dplyr::transmute(
      Site = GroupID,
      `Terms evaluated` = TermsEvaluated,
      `Terms flagged` = TermsFlagged,
      `Over-graded` = TermsOverGraded,
      `Under-graded` = TermsUnderGraded,
      `Largest gap` = scales::percent(MaxAbsDifference, accuracy = 0.1),
      `Max |z|` = round(MaxAbsZScore, 1),
      Pattern = Pattern
    ) %>%
    gt::gt() %>%
    gt::tab_options(table.width = gt::pct(100)) %>%
    gt::tab_source_note(
      "Sites flagged on two or more independent preferred terms. A single discrepant term is readily explained by case mix or chance; a pattern across several terms suggests the site applies the severity grading criteria differently from the rest of the study."
    )
}
```

## Flagged site/term detail

```{r detail}
dfTerm %>%
  dplyr::filter(Flagged) %>%
  dplyr::transmute(
    Site = GroupID,
    `Preferred term` = Term,
    `Site events` = SiteN,
    `Site Grade 3+` = scales::percent(SiteHighGrade, accuracy = 0.1),
    `Study Grade 3+` = scales::percent(StudyHighGrade, accuracy = 0.1),
    Gap = sprintf("%+.1f pp", Difference * 100),
    `z` = round(ZScore, 1),
    Direction = Direction
  ) %>%
  gt::gt() %>%
  gt::tab_options(table.width = gt::pct(100))
```

# Method notes and limitations

- **Grades are treated as reported.** No re-derivation from lab values or
  outcome data is attempted; the report measures internal consistency across
  sites, not clinical correctness.
- **The study is its own comparator.** If grading drifts study-wide, this report
  will not detect it — every site is compared to the study average.
- **The absolute-difference rule is asymmetric in practice.** Because the
  study-wide Grade 3+ proportion is only
  `r sprintf("%.1f%%", nStudyHigh * 100)`, a site cannot fall
  `r scales::percent(params$nDiffThreshold)` *below* the study average on a term
  whose study-wide Grade 3+ proportion is itself under
  `r scales::percent(params$nDiffThreshold)`. Under-grading on low-severity terms
  is therefore structurally hard to flag with a fixed percentage-point rule. The
  `z` column applies a volume-scaled binomial z-score instead, which stays
  symmetric across both tails; it is reported alongside the absolute rule so the
  two can be compared before a production threshold is chosen.
- **Volume thresholds bind hard at small sites.** Sites below
  `r params$nMinTermSite` events for a term are not evaluated on it, so a small
  site with a genuine grading problem may show no flags at all.
- **Multiplicity is not controlled.** With `r params$nTopTerms` terms and
  `r nSites` sites, some flagged pairs are expected by chance alone. Requiring
  two or more flagged terms per site is a deliberately crude guard against this.
