---
output:
  html_document:
    mathjax: null
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    css: styles.css
params:
  dfResults: NA
  dfMetrics: NA
  dfGroups: NA
  lListings: NA
---

```{r setup, include=FALSE} 
library(dplyr)
library(stringr)
library(tidyr)
library(gsm.kri)
library(gsm.qtl)
library(gt)
library(htmltools)
library(knitr)

knitr::opts_chunk$set(warning = FALSE, message = FALSE)


dfResults <- params$dfResults
dfMetrics <- params$dfMetrics
dfGroups <- params$dfGroups
lListings <- params$lListings
IE_num <- lListings$IE_num
IE_denom <- lListings$IE_denom
latest_snapshot = max(dfResults$SnapshotDate)
```

---
title: " Ineligible Participant Overview"
subtitle: "Study: `r unique(lListings[[1]]$studyid)`"
date: "Snapshot Date: `r latest_snapshot`"
---

# Ineligible Participant Overview

## Study Overview
```{r, echo=FALSE}
Eligibility_Overview(
  dfResults = dfResults,
  dSnapshot = latest_snapshot,
  strNum = "Ineligible Participants",
  strDenom = "Total Enrolled", 
  strQTL = "Current Ineligible Enrolled Rate"
)
```

## Time Series Chart
```{r, echo=FALSE, results='asis', fig.height=4}
gsm.kri::Widget_TimeSeries(
  dfResults = dfResults %>% mutate(Flag = NA),
  lMetric = as.list(dfMetrics),
  dfGroups = dfGroups,
  strOutcome = "Metric",
  bAddGroupSelect = FALSE,
  selectedGroupIDs = unique(dfResults$GroupID)
)
```

## Bar Charts {.tabset .tabset-pills}

### Site
```{r, echo = FALSE}
gsm.qtl::eligibility_groupBar(dfNum = IE_num, dfDenom = IE_denom, varGroupID = invid, strGroupLabel = "Site")
```

### Country
```{r, echo = FALSE}
gsm.qtl::eligibility_groupBar(dfNum = IE_num, dfDenom = IE_denom, varGroupID = country, strGroupLabel = "Country")
```

### Source
```{r, echo = FALSE}
gsm.qtl::eligibility_sourceBar(df = IE_num)
```

### Criteria/Site (EDC I/E data only)
```{r, echo = FALSE}
gsm.qtl::criteria_groupBar(df =  IE_num, varGroupID = invid, strGroupLabel = "Site")
```

### Criteria/Country (EDC I/E data only)
```{r, echo = FALSE}
gsm.qtl::criteria_groupBar(df =  IE_num, varGroupID = country, strGroupLabel = "Country")
```

### Site/Criteria (EDC I/E data only)
```{r, echo = FALSE}
gsm.qtl::criteria_groupBar(df =  IE_num, varGroupID = invid, strGroupLabel = "Site", bSwapAxes = TRUE)
```

### Country/Criteria (EDC I/E data only)
```{r, echo = FALSE}
gsm.qtl::criteria_groupBar(df =  IE_num, varGroupID = country, strGroupLabel = "Country", bSwapAxes = TRUE)
```

## Inclusion/Exclusion Listing
```{r, echo = FALSE}
# output the listing on the html
gsm.qtl::eligibility_listing(df = IE_num)

# grab the dataset to download
x <- gsm.qtl::eligibility_listing(df = IE_denom, download = TRUE)
csv_txt <- paste(utils::capture.output(utils::write.csv(x, row.names = FALSE)), collapse = "\n")# turn into a data-URI (single-file HTML friendly)
href <- base64enc::dataURI(charToRaw(csv_txt), mime = "text/csv;charset=utf-8")

knitr::asis_output(
  sprintf('<p><a class="btn btn-primary" download="eligibility_listing.csv" href="%s">
            ⬇️ Download CSV
          </a></p>', href)
)
```


```{r echo=FALSE}
toggle_toc <- system.file('report', 'lib', 'toggleTOC.js', package = "gsm.kri")
```

```{js, file={toggle_toc}, echo=FALSE}
```
