---
# pagetitle sets only the HTML <head><title>; the visible title and subtitle are
# emitted in the body so the knit_child pkgdown embed picks them up.
pagetitle: "Time to First Adverse Event"
output:
  html_document:
    mathjax: null
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    css: styles.css
params:
  dfResults: NA
  dfMetrics: NA
  dfGroups: NA
  dfBounds: NA
  lListings: NA
  strMetricID: "Analysis_kri0019"
---

```{r setup, include=FALSE}
library(dplyr)
library(gsm.kri)
library(gt)
library(plotly)

knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = FALSE)

dfResults <- params$dfResults %>% dplyr::filter(.data$MetricID == params$strMetricID)
dfMetrics <- params$dfMetrics %>% dplyr::filter(.data$MetricID == params$strMetricID)
lMetric <- as.list(dfMetrics)

strGroupLevel <- unique(dfResults$GroupLevel)
dSnapshotDate <- max(dfResults$SnapshotDate)
strStudyID <- unique(dfResults$StudyID)

# Re-derive the subject-level frame with the same function the metric uses, so
# the curve and the site table can never describe different cohorts.
dfInput <- Input_TimeToEvent(
  dfSubjects = params$lListings$Mapped_SUBJ,
  dfEvents = params$lListings$Mapped_AE,
  strGroupCol = if (identical(strGroupLevel, "Country")) "country" else "invid",
  strGroupLevel = strGroupLevel
)

dfCurve <- ttae_KaplanMeier(dfInput)
nMedian <- ttae_MedianTime(dfCurve)

nSubjects <- nrow(dfInput)
nEvents <- sum(dfInput$Numerator)
nPersonDays <- sum(dfInput$Denominator)
nHazard <- 100 * nEvents / nPersonDays

nHigh <- sum(dfResults$Flag > 0, na.rm = TRUE)
nLow <- sum(dfResults$Flag < 0, na.rm = TRUE)
nBelowAccrual <- sum(is.na(dfResults$Flag))
```

---
title: "Time to First Adverse Event"
subtitle: "Study: `r strStudyID` &nbsp;&middot;&nbsp; `r strGroupLevel`-level (`r lMetric$MetricID`)"
date: "Snapshot Date: `r dSnapshotDate`"
---

## Study Overview

```{r overview, results='asis'}
tibble::tibble(
  Measure = c(
    "Enrolled participants",
    "Participants with a post-enrollment AE",
    "Median time to first AE (Kaplan-Meier)",
    "Total days at risk",
    "Study-wide rate per 100 days at risk",
    paste0(strGroupLevel, "s flagged - unexpectedly SHORT time to AE"),
    paste0(strGroupLevel, "s flagged - unexpectedly LONG time to AE"),
    paste0(strGroupLevel, "s below the accrual threshold (not flagged)")
  ),
  Value = c(
    format(nSubjects, big.mark = ","),
    paste0(
      format(nEvents, big.mark = ","),
      " (", round(100 * nEvents / nSubjects), "%)"
    ),
    if (is.na(nMedian)) "not reached" else paste0(nMedian, " days"),
    format(nPersonDays, big.mark = ","),
    sprintf("%.2f", nHazard),
    as.character(nHigh),
    as.character(nLow),
    as.character(nBelowAccrual)
  )
) %>%
  gt::gt() %>%
  gt::tab_options(column_labels.hidden = TRUE, table.width = gt::pct(100)) %>%
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = "Value")
  ) %>%
  gt::as_raw_html() %>%
  cat()
```

::: {.alert .alert-info}
**Reading the score.** The Poisson score is on the *event-rate* scale, so its
sign runs opposite to the metric's name. A **negative** score means fewer first
AEs than expected for the observed days at risk, i.e. an unexpectedly **long**
time to first AE - the under-reporting direction, which carries the heaviest risk
weight. A **positive** score means an unexpectedly **short** time to first AE.
:::

## Time-to-Event Curve

Kaplan-Meier estimate of the probability of remaining adverse-event-free.
Participants with no post-enrollment AE are right-censored at their last
follow-up day rather than dropped, so groups with short follow-up are not
mistaken for groups with genuinely long event-free times.

```{r km-curve, fig.height=4.5}
vFlaggedLow <- dfResults$GroupID[!is.na(dfResults$Flag) & dfResults$Flag <= -2]
vFlaggedHigh <- dfResults$GroupID[!is.na(dfResults$Flag) & dfResults$Flag >= 1]

BuildCurve <- function(vGroups, strLabel) {
  dfSub <- dfInput %>% dplyr::filter(.data$GroupID %in% vGroups)
  if (nrow(dfSub) == 0) {
    return(NULL)
  }
  ttae_KaplanMeier(dfSub) %>% dplyr::mutate(Cohort = strLabel)
}

dfPlot <- dplyr::bind_rows(
  dfCurve %>% dplyr::mutate(Cohort = "All participants"),
  BuildCurve(vFlaggedLow, "Flagged - long time to AE"),
  BuildCurve(vFlaggedHigh, "Flagged - short time to AE")
)

vColors <- c(
  "All participants" = "#595959",
  "Flagged - long time to AE" = "#1F77B4",
  "Flagged - short time to AE" = "#D62728"
)

plotly::plot_ly(
  dfPlot,
  x = ~Time,
  y = ~Survival,
  color = ~Cohort,
  colors = vColors[intersect(names(vColors), unique(dfPlot$Cohort))],
  type = "scatter",
  mode = "lines",
  line = list(shape = "hv", width = 2),
  hovertemplate = paste0(
    "Day %{x}<br>Event-free: %{y:.1%}<extra>%{fullData.name}</extra>"
  )
) %>%
  plotly::layout(
    xaxis = list(title = "Days since enrollment", zeroline = FALSE),
    yaxis = list(
      title = "Probability AE-free",
      tickformat = ".0%",
      range = c(0, 1)
    ),
    legend = list(orientation = "h", y = -0.2),
    hovermode = "closest"
  ) %>%
  plotly::config(displayModeBar = FALSE)
```

## `r strGroupLevel`-Level Results

On the scatter plot each point is one `r tolower(strGroupLevel)`: the x axis is
total days at risk (exposure) and the y axis is the number of participants whose
first AE was observed. The shaded bands are the Poisson prediction bounds at the
metric's flagging thresholds, so a point below the lower band has recorded fewer
first AEs than its exposure predicts.

```{r charts, results='asis'}
lCharts <- MakeCharts(
  dfResults = dfResults,
  dfMetrics = dfMetrics,
  dfGroups = params$dfGroups,
  dfBounds = params$dfBounds
)

Report_MetricCharts(
  lCharts = lCharts[[params$strMetricID]],
  strMetricID = params$strMetricID
)
```

## Definition and Caveats

- **Time zero** is `firstparticipantdate` (enrollment). A participant's event is
  the earliest AE start date on or after that day; AEs dated before enrollment
  are ignored, the usual treatment-emergent definition.
- **Censoring**: participants with no post-enrollment AE contribute their full
  `timeonstudy` as days at risk with no event.
- **Model**: `gsm.core::Analyze_Poisson()`, a log-linked Poisson GLM of first-AE
  count on log(days at risk). The exposure coefficient is *fitted* rather than
  fixed at 1, so the expected count is
  `exp(b0) x (days at risk)^b1` and is not strictly proportional to exposure.
  The score is the deviance residual, and the prediction bounds above come from
  the same fit, so the two are consistent. Read the score as "relative to what
  comparable groups in this study recorded", not as a person-time hazard ratio.
- **Accrual gate**: groups with fewer than
  `r lMetric$AccrualThreshold` days at risk are scored but not flagged
  (`r nBelowAccrual` `r tolower(strGroupLevel)`s at this snapshot).
- A participant whose first AE falls on the enrollment date contributes zero days
  at risk. Those participants still count toward the numerator, so a group's rate
  can exceed what its documented exposure alone implies.
