---
output:
  html_document:
    mathjax: null
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    css: styles.css
params:
  dfResults: NA
  dfMetrics: NA
  dfGroups: NA
  lListings: NA
  nWindowDays: 90
---

```{r setup, include=FALSE}
library(dplyr)
library(gsm.kri)
library(plotly)
library(DT)
library(htmltools)
library(knitr)
library(jsonlite)

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

dfResults <- params$dfResults
lListings <- params$lListings
nWindowDays <- params$nWindowDays

Mapped_Death <- lListings$Mapped_Death
Mapped_SUBJ <- lListings$Mapped_SUBJ

# Country → site lookup for JS filtering (all enrolled sites in the country)
country_site_map <- Mapped_SUBJ %>%
  dplyr::distinct(country, invid) %>%
  dplyr::group_by(country) %>%
  dplyr::summarise(sites = list(invid), .groups = "drop") %>%
  tibble::deframe() %>%
  jsonlite::toJSON(auto_unbox = FALSE)

# Country → sites with >=1 premature death (within window). The scatter/buckets
# only ever render sites that had a premature death, so the filter banner reports
# this count over the enrolled-site total rather than implying all enrolled sites
# appear in the charts.
country_premature_site_map <- Mapped_Death %>%
  dplyr::filter(!is.na(.data$death_dy) & .data$death_dy <= nWindowDays) %>%
  dplyr::inner_join(
    Mapped_SUBJ %>% dplyr::distinct(.data$subjid, .data$country, .data$invid),
    by = "subjid"
  ) %>%
  dplyr::distinct(.data$country, .data$invid) %>%
  dplyr::group_by(.data$country) %>%
  dplyr::summarise(sites = list(.data$invid), .groups = "drop") %>%
  tibble::deframe() %>%
  jsonlite::toJSON(auto_unbox = FALSE)

# 0-indexed column position of invid in the DT widget (for JS filtering)
invid_col_idx <- 6L

nEnrolled <- nrow(Mapped_SUBJ)
nPremature <- sum(!is.na(Mapped_Death$death_dy) & Mapped_Death$death_dy <= nWindowDays)
nPrematureRate <- ifelse(nEnrolled > 0, 100 * nPremature / nEnrolled, 0)
latest_snapshot <- max(dfResults$SnapshotDate)
has_premature <- nPremature > 0

# Consistency guard: the charts recompute premature status from Mapped_Death at
# nWindowDays; the patient listing trusts pat0015 Flag==2 rows (flagged at
# analysis-time meta.WindowDays). A divergence means nWindowDays != the window
# that produced dfResults -> charts and listing describe different windows.
nFlagged <- sum(
  dfResults$MetricID == "Analysis_pat0015" & dfResults$Flag == 2,
  na.rm = TRUE
)
if (nFlagged != nPremature) {
  pd_CheckWindowConsistency(nWindowDays, nPremature, nFlagged)
}
```

---
title: "Premature Deaths Overview"
subtitle: "Study: `r unique(Mapped_SUBJ$studyid)`"
date: "Snapshot Date: `r latest_snapshot`"
---

# Premature Deaths Overview

## Overview

::: flag-container
::: {.flag .flag-red}
<div> `r nPremature` Premature Death(s) </div>
:::

::: {.flag .flag-green}
<div> `r nEnrolled - nPremature` Alive at Window </div>
:::
:::

```{r overview, echo=FALSE, results='asis'}
cat(sprintf(
  "- **Configured window:** %d days\n
   - **Total enrolled:** %d\n
   - **Premature deaths (within window):** %d\n
   - **Premature death rate:** %.1f%%\n",
  nWindowDays, nEnrolled, nPremature, nPrematureRate
))
```

```{r empty-state, echo=FALSE, results='asis', eval=!has_premature}
cat("\n> **No premature deaths in window.** All charts and the patient listing are empty for this snapshot.\n")
```

## Study {.tabset .tabset-pills}

### Buckets
```{r study-buckets, echo=FALSE, eval=has_premature}
pd_BucketBar(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "studyid", strGroupLabel = "Study")
```

### Rand -> Death
```{r study-scatter, echo=FALSE, eval=has_premature}
pd_RandToDeathScatter(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "studyid", strGroupLabel = "Study", dSnapshotDate = latest_snapshot)
```

### Reasons
```{r study-reasons, echo=FALSE, eval=has_premature}
pd_ReasonDist(Mapped_Death, nWindowDays, nEnrolled = nEnrolled)
```

## Country {.tabset .tabset-pills}

### Buckets
```{r country-buckets, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-country-buckets",
  pd_BucketBar(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "country", strGroupLabel = "Country")
)
```

### Rand -> Death
```{r country-scatter, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-country-scatter",
  pd_RandToDeathScatter(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "country", strGroupLabel = "Country")
)
```

## Site {.tabset .tabset-pills}

<div id="pd-filter-banner" style="display:none; background:#e3f2fd; border:1px solid #90caf9; border-radius:6px; padding:10px 16px; margin:16px 0; align-items:center; justify-content:space-between;">
  <span id="pd-filter-text" style="font-size:13px; color:#1565c0;"></span>
  <button id="pd-filter-reset" onclick="pdResetFilter()" style="background:#1a73e8; color:white; border:none; border-radius:4px; padding:4px 12px; cursor:pointer; font-size:12px;">✕ Show All Sites</button>
</div>

### Buckets
```{r site-buckets, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-site-buckets",
  pd_BucketBar(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "invid", strGroupLabel = "Site")
)
```

### Rand -> Death
```{r site-scatter, echo=FALSE, eval=has_premature}
htmltools::div(
  id = "pd-site-scatter",
  pd_RandToDeathScatter(Mapped_Death, Mapped_SUBJ, nWindowDays, strGroupCol = "invid", strGroupLabel = "Site")
)
```

## Patient Listing
```{r patient-listing, echo=FALSE}
pd_PatientListing(dfResults, Mapped_Death, Mapped_SUBJ)
```

```{r filter-js, echo=FALSE, results='asis', eval=has_premature}
cat(sprintf('
<script>
(function() {
  var countrySiteMap = %s;
  var countryPrematureSiteMap = %s;
  var invidColIdx = %d;
  var activeCountry = null;

  // Find the plotly div inside a container
  function getPlotlyDiv(containerId) {
    var container = document.getElementById(containerId);
    if (!container) return null;
    return container.querySelector(".plotly");
  }

  // Attach click handler to country buckets chart (max 5 retries)
  var attachRetries = 0;
  function attachCountryClick() {
    var el = getPlotlyDiv("pd-country-buckets");
    if (!el) {
      if (++attachRetries < 5) setTimeout(attachCountryClick, 500);
      return;
    }
    el.on("plotly_click", function(data) {
      var country = data.points[0].x;
      if (country === activeCountry) {
        pdResetFilter();
      } else {
        applyFilter(country);
      }
    });
  }

  function applyFilter(country) {
    activeCountry = country;
    var sites = countrySiteMap[country] || [];
    var prematureSites = countryPrematureSiteMap[country] || [];

    // Show banner. The charts only render sites with a premature death, so the
    // headline count is premature-death sites over the enrolled-site total.
    var banner = document.getElementById("pd-filter-banner");
    banner.style.display = "flex";
    document.getElementById("pd-filter-text").innerHTML =
      "\\ud83d\\udd0d <strong>Showing " + country + "</strong> \\u2014 " +
      prematureSites.length + "/" + sites.length +
      " sites with at least 1 premature death";

    // Highlight country bar: dim non-selected
    highlightCountryBar(country);

    // Filter country scatter to selected country only
    filterPlotlyChart("pd-country-scatter", [country]);

    // Filter site buckets
    filterPlotlyChart("pd-site-buckets", sites);

    // Filter site scatter
    filterPlotlyChart("pd-site-scatter", sites);

    // Filter patient listing
    filterPatientListing(sites);
  }

  function highlightCountryBar(country) {
    var el = getPlotlyDiv("pd-country-buckets");
    if (!el) return;
    var data = el.data;
    for (var i = 0; i < data.length; i++) {
      var opacities = data[i].x.map(function(x) {
        return x === country ? 1.0 : 0.3;
      });
      Plotly.restyle(el, {"marker.opacity": [opacities]}, [i]);
    }
  }

  // Store original trace data + layout for each chart on first filter
  var originalData = {};
  var originalLayout = {};

  function filterPlotlyChart(containerId, allowedValues) {
    var el = getPlotlyDiv(containerId);
    if (!el) return;
    // Cache original data + layout on first call
    if (!originalData[containerId]) {
      originalData[containerId] = JSON.parse(JSON.stringify(el.data));
    }
    if (!originalLayout[containerId]) {
      originalLayout[containerId] = JSON.parse(JSON.stringify(el.layout));
    }
    var orig = originalData[containerId];
    var matchAxisGlobal = null;
    var keptCategories = [];
    var seenCategory = {};
    var filtered = orig.map(function(trace) {
      // Determine which axis has categorical group values (strings)
      var matchAxis = null;
      if (trace.x && trace.x.length > 0 && typeof trace.x[0] === "string") {
        matchAxis = "x";
      } else if (trace.y && trace.y.length > 0 && typeof trace.y[0] === "string") {
        matchAxis = "y";
      }
      if (!matchAxis) return trace;
      matchAxisGlobal = matchAxis;

      var axisData = trace[matchAxis];
      var indices = [];
      axisData.forEach(function(val, idx) {
        if (allowedValues.indexOf(val) >= 0) {
          indices.push(idx);
          // Track kept categories in first-seen order to rebuild the axis
          if (!seenCategory[val]) { seenCategory[val] = true; keptCategories.push(val); }
        }
      });

      var newTrace = Object.assign({}, trace);
      newTrace.x = indices.map(function(i) { return trace.x[i]; });
      if (trace.y) newTrace.y = indices.map(function(i) { return trace.y[i]; });
      if (trace.text) newTrace.text = indices.map(function(i) { return trace.text[i]; });
      if (trace.marker && trace.marker.color && Array.isArray(trace.marker.color)) {
        newTrace.marker = Object.assign({}, trace.marker);
        newTrace.marker.color = indices.map(function(i) { return trace.marker.color[i]; });
      }
      return newTrace;
    });

    // Constrain the categorical axis to only the kept categories. Without this,
    // Plotly reuses the cached axis (and its computed range) and leaves an empty
    // tick/slot for every filtered-out site, so the bars shrink but the axis
    // still spans all study sites.
    var layout = JSON.parse(JSON.stringify(originalLayout[containerId]));
    if (matchAxisGlobal) {
      var axisName = matchAxisGlobal === "x" ? "xaxis" : "yaxis";
      layout[axisName] = Object.assign({}, layout[axisName] || {}, {
        categoryorder: "array",
        categoryarray: keptCategories,
        autorange: true
      });
      delete layout[axisName].range;
    }
    Plotly.react(el, filtered, layout);
  }

  function filterPatientListing(sites) {
    var tables = document.querySelectorAll(".dataTable");
    if (tables.length === 0) return;
    var dtApi = $(tables[tables.length - 1]).DataTable();
    var regex = "^(" + sites.join("|") + ")$";
    dtApi.column(invidColIdx).search(regex, true, false).draw();
  }

  // Global reset function (called by button onclick)
  window.pdResetFilter = function() {
    activeCountry = null;

    // Hide banner
    document.getElementById("pd-filter-banner").style.display = "none";

    // Reset country bar opacity
    var el = getPlotlyDiv("pd-country-buckets");
    if (el) {
      for (var i = 0; i < el.data.length; i++) {
        var allOnes = el.data[i].x.map(function() { return 1.0; });
        Plotly.restyle(el, {"marker.opacity": [allOnes]}, [i]);
      }
    }

    // Reset country scatter
    resetPlotlyChart("pd-country-scatter");

    // Reset site buckets
    resetPlotlyChart("pd-site-buckets");

    // Reset site scatter
    resetPlotlyChart("pd-site-scatter");

    // Reset patient listing
    var tables = document.querySelectorAll(".dataTable");
    if (tables.length > 0) {
      var dtApi = $(tables[tables.length - 1]).DataTable();
      dtApi.column(invidColIdx).search("").draw();
    }
  };

  function resetPlotlyChart(containerId) {
    var el = getPlotlyDiv(containerId);
    if (!el || !originalData[containerId]) return;
    // Restore the original layout so the full categorical axis returns
    Plotly.react(el, originalData[containerId], originalLayout[containerId] || el.layout);
  }

  // Initialize when DOM is ready
  if (document.readyState === "complete") {
    attachCountryClick();
  } else {
    window.addEventListener("load", attachCountryClick);
  }
})();
</script>
', country_site_map, country_premature_site_map, invid_col_idx))
```
