---
title: "Site KRI Report"
author: "[gsm.kri](https://gilead-public.github.io/gsm.kri) Example"
description: "Example of a Site KRI Report generated using standard KRIs in gsm.kri"
index: 1
date: "`r format(Sys.time(), '%B %d, %Y %H:%M:%S %Z')`"
output:
  html_document:
    mathjax: null
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    css: styles.css
---

# Set Up

This page provides a sample Site KRI Report generated using the standard KRIs included in the `gsm.kri` package. Expand the "Setup" section below to see the code used to generate the report. Or scroll down for the standard KRI report output.

The example calculates `Analysis_srs0002` from the deterministic longitudinal
`gsm.core::reportingActionLog` fixture. The existing Site Overview displays the
adjusted score immediately after the original Site Risk Score.

<details>
<summary>Setup</summary>

```{r}
# Load libraries
library(gsm.core)
library(gsm.kri)
library(here)

latest_snapshot <- max(gsm.core::reportingResults$SnapshotDate)
weights <- gsm.kri::MakeWeights(gsm.core::reportingMetrics)
current_kri_results <- gsm.core::reportingResults %>%
  dplyr::filter(
    .data$SnapshotDate == latest_snapshot,
    .data$GroupLevel == "Site",
    grepl("^Analysis_kri", .data$MetricID),
    .data$MetricID %in% weights$MetricID
  )
action_weighted_score <- gsm.kri::CalculateActionRiskScore(
  dfResults = current_kri_results,
  dfWeights = weights,
  dfActionLog = gsm.core::reportingActionLog,
  strMissingState = "error"
) %>%
  dplyr::mutate(
    StudyID = unique(current_kri_results$StudyID),
    SnapshotDate = latest_snapshot
  )

# Per-KRI detail explains each adjusted score in the Site Overview.
action_score_detail <- gsm.kri::MakeActionRiskScoreDetail(
  dfResults = current_kri_results,
  dfWeights = weights,
  dfActionLog = gsm.core::reportingActionLog,
  strMissingState = "error"
)

site_results <- dplyr::bind_rows(
  gsm.core::reportingResults,
  action_weighted_score
)

## Site Report
lCharts <- gsm.kri::MakeCharts(
  dfResults = site_results,
  dfGroups = gsm.core::reportingGroups,
  dfMetrics = gsm.core::reportingMetrics,
  dfBounds = gsm.core::reportingBounds
)
```

</details>

# Report

```{r, echo=FALSE, results='asis'}
## Render example report inline using knit_child
child_env <- list2env(
  list(
    params = list(
      lCharts = lCharts,
      dfResults = gsm.kri::FilterByLatestSnapshotDate(site_results),
      dfGroups = gsm.core::reportingGroups,
      dfMetrics = gsm.core::reportingMetrics,
      strComparisonRiskMetric = "Analysis_srs0002",
      strComparisonRiskLabel = "Adjusted Risk Score",
      dfRiskScoreDetail = action_score_detail
    )
  ),
  parent = environment()
)
report_kri <- knitr::knit_child(
  system.file("report", "Report_KRI.Rmd", package = "gsm.kri"),
  envir = child_env,
  quiet = TRUE
)
cat(report_kri, sep = "\n")
```