---
title: "Time to First AE Report"
author: "[gsm.kri](https://gilead-public.github.io/gsm.kri) Example"
description: "Example Time to First Adverse Event report generated with gsm.kri (kri0019)"
index: 5
date: "`r format(Sys.time(), '%B %d, %Y %H:%M:%S %Z')`"
output:
  html_document:
    mathjax: null
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    css: styles.css
---
# Set Up

This page provides a sample Time to First Adverse Event report, generated from the
standard `gsm.core::lSource` example data with the new `kri0019` metric. Expand the
"Setup" section below to see the code used to generate it, or scroll down for the
report output.

The metric asks a different question from `kri0001` (Adverse Event Rate): rather than
how *many* AEs a site records per day on study, it asks how *long* a participant is
on study before their first AE is recorded. A site can post a study-average AE rate
while recording nothing for its first several weeks, and only this metric sees that.

<details>
<summary>Setup</summary>

```{r}
# Load libraries
library(gsm.core)
library(gsm.mapping)
library(gsm.kri)
library(gsm.reporting)
library(dplyr)

# --- Step 1: Map the raw example data ----------------------------------------
# kri0019 needs AE start dates (Mapped_AE$aest_dt) plus each participant's
# enrollment date and follow-up duration (Mapped_SUBJ). No mapping changes were
# required to add this metric -- gsm.mapping already carries all three.
core_mappings <- c("AE", "COUNTRY", "ENROLL", "SITE", "STUDY", "SUBJ")

mappings_wf <- MakeWorkflowList(
  strNames = core_mappings,
  strPath = "workflow/1_mappings",
  strPackage = "gsm.mapping",
  bExact = TRUE
)
lRaw <- Ingest(gsm.core::lSource, CombineSpecs(mappings_wf))
lMapped <- RunWorkflows(mappings_wf, lRaw)

# --- Step 2: Run the site and country time-to-first-AE metrics ---------------
metrics_wf <- MakeWorkflowList(
  strNames = c("kri0019", "cou0019"),
  strPath = "workflow/2_metrics",
  strPackage = "gsm.kri",
  bExact = TRUE
)
lAnalyzed <- RunWorkflows(metrics_wf, c(lMapped, list(lWorkflows = metrics_wf)))

# --- Step 3: Build the reporting frames --------------------------------------
# kri0019 declares `AnalysisType: poisson`, which is what makes MakeBounds
# reach for Analyze_Poisson_PredictBounds instead of the normal-approximation
# bounds used by the rest of the KRIs.
reporting_wf <- MakeWorkflowList(
  strNames = c("Results", "Metrics", "Bounds", "Groups"),
  strPath = "workflow/3_reporting",
  strPackage = "gsm.reporting"
)
lReporting <- RunWorkflows(
  reporting_wf,
  c(lMapped, list(lAnalyzed = lAnalyzed, lWorkflows = metrics_wf))
)

dfResults <- lReporting$Reporting_Results |>
  FilterByLatestSnapshotDate()

# --- Step 4: The listings the report re-derives its cohort from --------------
# The report calls Input_TimeToEvent() on these, the same function the metric
# uses, so the Kaplan-Meier curve and the site table describe one cohort.
lListings <- list(
  Mapped_SUBJ = lMapped$Mapped_SUBJ,
  Mapped_AE = lMapped$Mapped_AE
)
```

</details>

# Site-Level Report

```{r, echo=FALSE, results='asis'}
child_env <- list2env(
  list(
    params = list(
      dfResults = dfResults,
      dfMetrics = lReporting$Reporting_Metrics,
      dfGroups = lReporting$Reporting_Groups,
      dfBounds = lReporting$Reporting_Bounds,
      lListings = lListings,
      strMetricID = "Analysis_kri0019"
    )
  ),
  parent = environment()
)
report_ttae <- knitr::knit_child(
  system.file("report", "Report_TimeToAE.Rmd", package = "gsm.kri"),
  envir = child_env,
  quiet = TRUE
)
cat(report_ttae, sep = "\n")
```
