---
title: "AE Grading Report"
author: "[gsm.kri](https://gilead-public.github.io/gsm.kri) Example"
description: "Example AE severity grading report generated with gsm.kri"
index: 5
date: "`r format(Sys.time(), '%B %d, %Y %H:%M:%S %Z')`"
output:
  html_document:
    mathjax: null
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    css: styles.css
---
# Set Up

This page provides a sample AE Grading Report generated using the `gsm.kri` package. Expand the "Setup" section below to see the code used to generate the report. Or scroll down for the standard report output.

The report is a companion to the two site-level grading metrics, `kri0016` (High-Grade AE Proportion) and `kri0017` (Low-Grade AE Proportion). Those metrics flag sites whose overall severity mix differs from the study; this report adds the term-level detail they cannot show.

> **Note on the example data.** The `gsm.core` example data carries only two placeholder preferred terms (`term1`, `term2`) and no site-level grading behaviour, so it cannot demonstrate the term-level analysis. This page therefore simulates the AE severity grades and preferred terms with `Sim_AEGrading()`, keeping the real subject/site structure and per-site AE burden. A handful of sites are given deliberate grading patterns so the report has something to find. Every number below is illustrative; the mechanics are real.

<details>
<summary>Setup</summary>

```{r}
# Load libraries
library(dplyr)
library(purrr)
library(tibble)
library(gsm.core)
library(gsm.kri)
library(gsm.mapping)

source("util/Sim_AEGrading.R")

# Map the example source data
mappings_wf <- workr::MakeWorkflowList(
  strNames = c("AE", "SUBJ", "SITE", "STUDY", "ENROLL", "COUNTRY", "DATAENT"),
  strPath = "workflow/1_mappings",
  strPackage = "gsm.mapping"
)

mappings_spec <- gsm.mapping::CombineSpecs(mappings_wf)
lRaw <- gsm.mapping::Ingest(gsm.core::lSource, mappings_spec)
mapped <- workr::RunWorkflows(mappings_wf, lRaw)

# Simulate a realistic grading scenario over the real site structure
sim <- Sim_AEGrading(mapped$Mapped_AE, mapped$Mapped_SUBJ)
mapped$Mapped_AE <- sim$AE

# Run the High-Grade AE Proportion metric so the report can mark flagged sites
kri0016 <- workr::RunWorkflow(
  workr::MakeWorkflowList("kri0016", strPath = "workflow/2_metrics", strPackage = "gsm.kri")[[1]],
  mapped
)
```

</details>

```{r, echo=FALSE, results='asis'}
## Render example report inline using knit_child
child_env <- list2env(
  list(
    params = list(
      dfAE = mapped$Mapped_AE,
      dfSubj = mapped$Mapped_SUBJ,
      strStudyID = unique(mapped$Mapped_SUBJ$studyid)[1],
      dfFlagged = kri0016$Analysis_Flagged,
      nMinAE = 20,
      nTopTerms = 10,
      nMinTermStudy = 50,
      nMinTermSite = 10,
      nDiffThreshold = 0.20
    )
  ),
  parent = environment()
)
report_ae_grading <- knitr::knit_child(
  system.file("report", "Report_AEGrading.Rmd", package = "gsm.kri"),
  envir = child_env,
  quiet = TRUE
)
cat(report_ae_grading, sep = "\n")
```
