---
title: "AE Grading Report"
author: "[gsm.kri](https://gilead-public.github.io/gsm.kri) Example"
description: "Example AE severity grading report generated with gsm.kri"
index: 5
date: "`r format(Sys.time(), '%B %d, %Y %H:%M:%S %Z')`"
output:
  html_document:
    mathjax: null
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    css: styles.css
---
# Set Up

This page provides a sample AE Grading Report generated using the `gsm.kri` package. Expand the "Setup" section below to see the code used to generate the report. Or scroll down for the standard report output.

The report is the visual companion to the two site-level grading metrics, `kri0016` (High-Grade AE Proportion) and `kri0017` (Low-Grade AE Proportion). It is produced by `Report_AEGrading()`, which is wired up as the `report_aegrading` workflow module.

> **Note on the example data.** The `gsm.core` example data has a realistic study-wide grade distribution, but grades are assigned independently of site, so no site deviates from the study and the report has nothing to find. This page therefore redraws `aetoxgr` with `Sim_AEGrading()`, keeping the real subject/site structure and per-site AE burden while giving a few sites deliberate over- and under-grading behaviour. Every number below is illustrative; the mechanics are real.

<details>
<summary>Setup</summary>

```{r}
# Load libraries
library(gsm.core)
library(gsm.mapping)
library(gsm.kri)
library(gsm.reporting)
library(dplyr)
library(tibble)

source("util/Sim_AEGrading.R")

# --- Step 1: Map raw data (real gsm.mapping pipeline) ------------------------
core_mappings <- c(
  "AE", "COUNTRY", "DATAENT", "ENROLL", "SITE", "STUDY", "SUBJ"
)

mappings_wf <- MakeWorkflowList(
  strNames = core_mappings,
  strPath = "workflow/1_mappings",
  strPackage = "gsm.mapping"
)
lRaw <- Ingest(gsm.core::lSource, CombineSpecs(mappings_wf))
lMapped <- RunWorkflows(mappings_wf, lRaw)

# --- Step 2: Simulate site-level grading behaviour (example only) ------------
sim <- Sim_AEGrading(lMapped$Mapped_AE, lMapped$Mapped_SUBJ)
lMapped$Mapped_AE <- sim$AE

# --- Step 3: Run the AE grading metrics --------------------------------------
metric_names <- c("kri0016", "kri0017")
metrics_wf <- MakeWorkflowList(
  strNames = metric_names,
  strPath = "workflow/2_metrics",
  strPackage = "gsm.kri"
)
lAnalyzed <- RunWorkflows(metrics_wf, c(lMapped, list(lWorkflows = metrics_wf)))

# --- Step 4: Build reporting frames (real gsm.reporting pipeline) ------------
reporting_wf <- MakeWorkflowList(
  strNames = c("Results", "Metrics", "Bounds", "Groups"),
  strPath = "workflow/3_reporting",
  strPackage = "gsm.reporting"
)
lReporting <- RunWorkflows(
  reporting_wf,
  c(lMapped, list(lAnalyzed = lAnalyzed, lWorkflows = metrics_wf))
)

dfResults <- lReporting$Reporting_Results |>
  FilterByLatestSnapshotDate()

# --- Step 5: Assemble the listings consumed by the report --------------------
lListings <- list(
  Mapped_AE = lMapped$Mapped_AE,
  Mapped_SUBJ = lMapped$Mapped_SUBJ
)
```

</details>

```{r, echo=FALSE, results='asis'}
## Render example report inline using knit_child
child_env <- list2env(
  list(
    params = list(
      dfResults = dfResults,
      lListings = lListings,
      strMetricID = "Analysis_kri0016",
      nMinAE = 20
    )
  ),
  parent = environment()
)
report_ae_grading <- knitr::knit_child(
  system.file("report", "Report_AEGrading.Rmd", package = "gsm.kri"),
  envir = child_env,
  quiet = TRUE
)
cat(report_ae_grading, sep = "\n")
```
